\subsection{Executive Duties}

  

1.1.1.1           The  Executive  of  the  GSA  shall  be  comprised  of  a President, Vice President Operations and Administration, Vice  

         President   Student   Affairs,   Vice   President   Academic,   Vice  

         President Finance and Vice President External. An Aboriginal  

         Liaison will convene with the GSA in a unique way, outlined in  

         Section 1.2 Aboriginal Liaison.   

  

1.1.2. All Executives members  

  

1.1.2.1           All executive members are accountable to the executive,  

         GSA Council and the graduate student body. The President and  

         Vice Presidents all shall:   

  

         i)       Be     elected      annually       in    accordance         with     Policy       2.  

                  Elections and Referenda.   

  

         ii)       Sit   on   committees   as   described   by   the   Policy   1.3  



                   Committee Representation .   

  

         iii)     Report   activities   of   their   position   to   GSA   Council  

                  monthly as prescribed in the Policy 5.1 Meetings .   

  

         iv)      Be voting members of Course Council.   

  

         v)       Actively   participate   in   course   council   and   executive  

                  meetings according to Policy 5. Meetings .   

  

         vi)      Read  and  understand  the  transition  manual  provided  to  



                  them  upon  election  to  the  GSA  executive  according  to  



                  Policy 3.4 Transition Manuals .   

  

         vii)     Create  and  update  this  Transition  Manual  during  their  

                  term in office for executive  members  assuming the  role  

                  after   them   in   according   with   Policy   3.4   Transition  

                  Manuals .   

  



                                                  3  

                                      

                                    Graduate Students’ Association  

                                   Executive Duties Policy Manual  

  


----------------------- Page 4-----------------------

viii)    Conduct  themselves  in  a  professional  and  constructive  

         manner   in   representing   GSA   and   the   University   of  

         Saskatchewan.   

  

ix)      Uphold the confidentiality of sensitive matters related to  

         the GSA  as an organization, its  executive  and  members  

         as described in Policy 3.7 Confidentiality.   

  

x)       Act as an ambassador of the GSA and a role model for all  

         students.   

  

xi)      To be responsible for the actions and the guidance of the  

         GSA.   

  

  

xii)     To  be  responsible  for  all  administrative  duties  of  the  

         GSA in the event that paid help is unavailable.   

  

xiii)    To promote public awareness of the GSA as described in  



         Policy 3. Communications.   

  

xiv)     To  consult  with  University  of  Saskatchewan  Students’  

         Union  counterparts  on  issues  of  common  interest  in  

         accordance with the Policy 3. Communications.   

  

xv)      Be vested with all executive powers, including the right  

         to negotiate contracts on behalf of the GSA, staffing, and  

         the right to delegate authority; all of which are subject to  

         ratification  by  GSA  Council.  The  Executive  shall  be  

         empowered to act in place of the GSA Council in dealing  

         with routine business   

  

xvi)     To  act  professionally  and  courteously  in  all  activities  

         relation  to  position  duties  and  in  dealings  with  each  

         other.  Threats  and  violence  of  any  kind  are  deemed  

         inappropriate and disciplinary action will be taken by the  

         executive.   

  

xvii)   To      perform       such     other     out-of-scope         duties     as    are  

         assigned by the General Council of the GSA subject to a  



                                        4  

                            

                          Graduate Students’ Association  

                          Executive Duties Policy Manual  

  


----------------------- Page 5-----------------------

                  50% plus one majority vote in GSA Council.   

  

1.1.3. President  

  

1.1.3.1           The  duties  of  the  President  shall  include,  but  are  not  

         limited to:   

  

         i)       To be accountable for the actions and the guidance of the  

                  GSA Council and other Executives.  

  

         ii)      To  ensure  that  the  responsibilities  of  each  executive  

                  position are being met.   

  

         iii)     To be responsible for performing or delegating the duties  



                  of any executive position when the duties are not being  



                  met or the position is vacant.   

  

         iv)      To   co-ordinate   all   business   with   representatives   on  



                  university  committees  and  boards  in  accordance  with  



                  Policy 1.3 Committee Representation .   



         vi)      To  present  objectives  for  the  Course  Council  and  the  

                  Executive        at    the    Annual       General       Meeting        and     to  

                  publicize  the  general  progress  of  the  GSA  at  the  last  

                  general meeting before the new president takes office in  

                  the spring as outlined in Policy 3. Communications .   

  

         vii)     To be a co-signer of cheques in accordance with Policy 8.  

                  Finance .   

  

         viii)    To  reprimand  executive  members  when  an  executive  

                  member fails to meet their executive commitments.   

  

         ix)      Oversee  the  supervision  of  GSA  Staff  as  outlined  in  



                  Policy 7. Employees and Volunteers.   

  

         x)       Temporarily  suspend  and  assume  the  responsibilities  of  

                  any       other       executive         member,          with       immediate  



                                                  5  

                                      

                                    Graduate Students’ Association  

                                   Executive Duties Policy Manual  

  


----------------------- Page 6-----------------------

                   notification, in case of emergency until a meeting of the  

                   executive can convene and for a period of no longer than  

                   one  week.  Emergencies  can  include  but  are  not  limited  

                   to:   

  

                            a. Reprimands.   

  

                            b. Conflict Mitigation.   

  

                            c. Inappropriate and unprofessional behavior.   

  

                            d. Failure to meet the duties and responsibilities   

  

                            e. Other unforeseen circumstances   

  

         xi)       To act as the general manager of the GSA.   

  

         xii)      To  actively  participate  in  the  financial  planning  and  

                   budgeting of the GSA.   

  

To produce, in consultation with the Vice Presidents, an annual report  

about the GSA operations for the GSA members and stakeholders in  

accordance with Policy 3. Communications .  

  

1.1.4. Vice President Operations and Communications  

1.1.4.1            The     duties      of    the    Vice      President        Operations         and  

         Communications shall include, but are not limited to:  

  

         i)        Assume the duties of president in the president’s absence.   

         ii)       To  act  as  recording  secretary  for  GSA  Executive,  GSA  

                   Council, and general meetings and to have knowledge of  

                   Roberts  Rules  of  Order  in  accordance  with  Policy  5.  

                   Meetings .   

  

         ii)       Coordinate   GSA   Council   Meetings,   ratifications   and  

                   track     attendance        in    accordance         with     the   Policy   5.  

                   Meetings .   

  

         iii)      To be a co-signer of cheques in accordance with Policy 8.  

                   Finance .   

  



                                                   6  

                                      

                                    Graduate Students’ Association  

                                    Executive Duties Policy Manual  

  


----------------------- Page 7-----------------------

         iv)      Appoint  a  GSA  Council  Chairperson,  Chief  Electoral  

                  Officer  and  Chief  Returning  Officer  for  GSA  Council  

                  Meetings,  Elections  and  Referenda  in  accordance  with  

                  Policies 5. Meetings and 2. Elections and Referenda.   

  

  

  

         v)       Organize executive meetings and internal communication  

                  between  the  Executive  and  Staff  in  accordance  with  

                  Policies 5. Meetings and 3. Communications.   

  

         vi)      Organize communication with the graduate student body  

                  and  the  university  community  through  emails,  posters  

                  and   the   GSA   website  in   accordance  with  Policy   3.  

                  Communication.   

  

         vii)     Act  as  the  direct  supervisor  of  the  GSA  Commons  

                  Coordinators  and  Office  Administrator  as  outlined  in  

                  Policies      6.   GSA      Commons   and            7.   Employees   and  

                  Volunteers.   

  

         viii)    Temporarily suspend and take over the responsibilities of  

                  the  President  in  case  of  emergency,  with  immediate  

                  notification, until a meeting of the executive can convene  

                  and for a period of no longer than one week.   

1.1.5. Vice President Student Affairs  

1.1.5.1           The  duties  of  the  Vice  President  Student  Affairs  shall  

         include, but not limited to:   

  

         i)       Act as a liaison officer within the University Community  

                  relating to non-academic issues.  

  

         ii)      Establish and maintain liaison with graduate students in  

                  each department via GSA Council.   

  

  

         iii)     To  be  responsible  for  the  recruitment  of  new  GSA  

                  Council representatives.   

  

         iv)      To oversee the ratification of campus clubs as outlined in  



                                                 7  

                                     

                                   Graduate Students’ Association  

                                  Executive Duties Policy Manual  

  


----------------------- Page 8-----------------------

                  Policy 4. Student Services.   

  

         v)       To     develop       a    program       of    social      events      for    the  

                  enhancement  of  the   graduate  student  experience  and  

                  promote inter-cultural and inter-disciplinary camaraderie.   

  

         vi)      To facilitate efficient communication between the GSA,  

                  College of Graduate Studies and Research, the University  

                  of Saskatchewan and GSA members at large.   

  

         vii)     To   coordinate   an   orientation   for   incoming   graduate  



                  students  in  September  and  January  in  accordance  with  



                  Policy 4. Student Services .   

  

         viii)    To  assist  in  integration  and  clear  communication  with  

                  new GSA members.   

  

         ix)      To  be  an  advocate  for  graduate  student  non-academic  

                  grievances in accordance with Policy 4. Student Services .   

  

         x)       To     address      issues     related     to    graduate       students      as  

                  employees of the University of Saskatchewan and ensure  

                  that University Policies and Provincial and Federal Laws  

                  are upheld.   

  

         xi)      To promote equality of graduate students.   

  

         xii)     To  oversee  regulations  and  policies  for  non-academic  

                  appeals and grievances.   

         xiii)    To  be  versed  in  the  University  Policies  on  relevant  

                  matters   including   but   not   limited   to   Teaching   and  

                  Research  Assistant  hourly  rates  and  hours;  tuition;  on  

                  campus housing.  

1.1.6. Vice President Academic  

1.1.6.1           The duties of the Vice President Academic shall include,  

         but are not limited to:   

  

         i)       To     act    as   a    liaison     officer     within      the    university  



                                                 8  

                                     

                                   Graduate Students’ Association  

                                  Executive Duties Policy Manual  

  


----------------------- Page 9-----------------------

                  community,           the    College        of    Graduate        Studies       and  

                  Research   and   the   University   of   Saskatchewan,   with  

                  respect to academic issues.   

  

         ii)      To     be    an     advocate       for    graduate       student      academic  

                  grievances in accordance with Policy 4. Student Services   

  

         iii)     To organize academic workshops and conferences.   

  

  

         iv)      To oversee regulations and policies for academic appeals  

                  and grievances.   

         v)       Oversee  the  administration  of  the  GSA  Travel  Grant  as  

                  per Policy 4. Student Services.  

         vi)      Oversee  the  administration  of  the  GSA  Bursary  as  per  

                  Policy 4. Student Services.   

                    

1.1.7  Vice President Finance   

  

1.1.7.1 The duties of the Vice President Finance shall include, but are  

          not limited to:   

  

         i)       To      receive      GSA        money        and     make       payments         in  



                  accordance  with  the  yearly  budget  approved  by  GSA  



                  Council  and  the  General  Assembly  in  accordance  with  



                  Policy 8. Finance .   

  

         ii)      To   record   and   publicize   GSA   financial   records   in  



                  accordance   with   Policies   3.   Communication   and   8.  



                  Finance .   

  

         iii)     To  present  an  updated  breakdown  of  the  budget  to  the  



                  GSA Executive and Course Council in accordance with  



                  Policies 5. Meetings and 8. Finance.   

  

         iv)      To ensure that the GSA operates in accordance with the  

                  Non-Profit Corporations Act.   

  



                                                  9  

                                      

                                    Graduate Students’ Association  

                                   Executive Duties Policy Manual  

  


----------------------- Page 10-----------------------

         v)       To coordinate fundraising efforts.   

  

         vi)      Ensure  that  the  annual  budget  is  approved  by  GSA  

                  Council at the annual general meeting in accordance with  

                  Policy 8. Finance .   

  

         vii)     To  be  responsible  for  the  purchase  and  maintenance  of  

                  liability insurance.   

  

         viii)    To be a co-signer of cheques in accordance with Policy 8.  

                  Finance .   

           



         ix)      Oversee  the  administration  of  the  GSA  Bursary  as  per  

                  Policy 4. Student Services.   

  

1.1.8  Vice President External  

  

1.1.8.1           The  duties of the  Vice  President  External  shall  include,  

         but are not limited to:   

  

         i)       To  act  as  a  liaison  officer  between  the  GSA  executive  

                  and the National Executive of the Canadian Federation of  

                  Students.   

  

         ii)      To  serve  on  the  executive  of  Canadian  Federation  of  

                  Students        -   Saskatchewan           as    either     the    Local      101  

                  representative or any other elected position.   

  

         iii)     To  act  as  a  liaison  officer  between  the  GSA  executive  

                  and the National Graduate Caucus executive.   

         iv)      To  oversee  the  compilation  of  the  GSA  promotional  

                  materials  at  the  annual  orientation  event  as  outlined  in  

                  Policy 3. Communications.   

         v)       To  be  responsible  for  initiating  and  maintaining  liaison  

                  activities        with       local,      provincial,         and       national  

                  organizations both on and off campus.   

         vi)      Negotiate the Health and Dental Plan in Accordance with  



                                                 10  

                                      

                                    Graduate Students’ Association  

                                   Executive Duties Policy Manual  

  


----------------------- Page 11-----------------------

           Policy 4. Student Services.   

vii)       To  attend  at  least  one  Canadian  Federation  of  Students  

           National  Meeting  and  the  National  Graduate  Caucus  

           Stand-Alone Meeting as a Representative of Local 101.   

viii)      To  update  and  maintain  the  constitution  in  accordance  

           with Policy 3. Communication.   

ix)        To  represent  GSA  at  Canadian  Federation  of  Students  

           Committee  

x)         To be a liaison between the GSA and other national and  

           international student unions in accordance with Policy 3.  

           Communication.   

  

  

  

  

  

  

  

  

  

  

  

  

  

  

  

  

  

  

  

  

  

  

  

  

  

  

  

  

  

  

  

  

  

  

  

  

  



                                                 11  

                                  

                                Graduate Students’ Association  

                                Executive Duties Policy Manual  

  


----------------------- Page 12-----------------------

                         1.2      Aboriginal and Indigenous Student Liaison   

  

1.2.1.1            The duties of the Indigenous Student Liaison shall include, but  

         are not limited to:   

  

         i)        To act as a liaison officer between the GSA executive and the  

                   Aboriginal Graduate Students' Association   

  

         ii)       To create and maintain the Aboriginal and Indigenous Graduate  

                   Students’ Council.   

  

         iii)      To      increase       the     presence        of    Aboriginal          and     Indigenous  

                   Graduate  Student  presence  on  campus  in  accordance  with  

                   Policy 3. Communication.   

  

         iv)       Help to ensure that Aboriginal content is included in the Annual  

                   GSA Orientation in accordance with Policy 4. Student Services.   

  

         v)        To  communicate  with  the  Canadian  Federation  of  Students  - 

                   Saskatchewan Aboriginal  Liaison, the  Chair of  the  Aboriginal  

                   Caucus   of   the   Canadian   Federation   of   Students   and   the  

                   Aboriginal National Executive Representative of the Canadian  

                   Federation of Students.   

         vi)       Work  with  the  Vice  President  Student  Affairs  on  the  annual  

                   orientation event.  

         vii)      Assist  the  Vice  Presidents  Student  Affairs,  and  Academic  on  

                   issues involving Aboriginal and Indigenous students.  

         viii)     Recruit new GSA Council Representatives from the Aboriginal  

                   community.  

                     

  

  

  

  

  

  

  

  

  

  

  

  



                                                         12  

                                        

                                      Graduate Students’ Association  

                                     Executive Duties Policy Manual  

  


----------------------- Page 13-----------------------

                         1.3       Committee Representation   

  

1.3.1.1            The GSA represents the graduate student body on a number of  

         committees within the University. The list below is not exhaustive, as  

         the  committee  structure  of  the  University  and  GSA  are  fluid.  The  

         president  will  appoint  GSA  members  to  committees  as  needed.  It  is  

         the  responsibility  of  the  following  Executive  members  to  sit  on  or  

         designate representation on the following committees:   

  

1.3.1.2            President   

  

         i)        Annual Giving Campaign Steering Committee.   

  

         ii)       Arts and Science By-laws Committee.   

  

         iii)      Campus Advisory Board for Institutional Systems (CABIS).   

  

         iv)       College of Graduate Studies and Research Executive Council.   

  

         v)        College Quarter Steering Committee.   

  

              a.       Undergraduate Residence Committee.   

              b.        Graduate House Residence Committee.   

  

              c.        College Quarter Master Plan Committee.   

  

         ii)       Degree Works.   

  

         iii)      Dispute Resolution Team.   

  

         iv)       Marquis Hall Renewal and Food Service Committee.   

  

         v)        On Campus News Editorial Board.   

  

         vi)       Planning and Priorities Committee of Council.   

  

         vii)      Policy Review Committees:   

  

              a.       Non-Academic Conduct.   

  

              b.        Conduct in Research.   

              c.        Tuition Principles.   

  

         viii)     Student Evaluation of Educational Quality (SEEQ) Committee.   



                                                        13  

                                       

                                     Graduate Students’ Association  

                                    Executive Duties Policy Manual  

  


----------------------- Page 14-----------------------

  

  

  

  

          ix)       University Learning Centre Advisory Board.   

  

          x)        Voting Member – University Council.   

  

          xi)       Voting Member – University Senate.   

          xii)      Vision 2057 Committee.   

  

1.3.1.3             Vice President Operations and Administration   

  

          i)        GSA Bursary Selection   

  

          ii)       GSA Elections Committee   

  

          iii)      College  of  Graduate  Studies  and  Research  Admissions  and  

                    Recruitment   

  

          iv)       College of Graduate Studies and Research Student Affairs   

  

          v)        College of Graduate Studies and Research Graduate Programs   

  

          vi)       Copyright Advisory   

  

          vii)      Teaching and Learning Committee of Council   

  

1.3.1.4             Vice President Student Affairs   

  

          i)        College of Graduate Studies and Research Interdisciplinary   

  

          ii)       Orientation   

  

          iii)      Academic Support   

  

          iv)       Campus Advisory Board for Institutional Systems   

  

          v)        Academic Integrity Awareness Week   

  

1.3.1.5             Vice President Academic   

  

          i)        University Council   

  



                                                          14  

                                         

                                       Graduate Students’ Association  

                                      Executive Duties Policy Manual  

  


----------------------- Page 15-----------------------

           ii)        Research, Scholarly and Artistic Work   

  

           iii)       Academic Programs   

  

           iv)        Graduate Council   

  

  

  

 1.3.1.6              Vice President Finance   

  

           i)         GSA Finance Committee   

  

           ii)        College of Graduate Studies and Research Awards   

  

 1.3.1.7              Vice President External   

  

           i)         International Activities Committee   

                               

                             1.4        Consistency  

  

 1.4.1                This Policy  shall not supersede or preclude policies governing  

distribution  of  funds,  personal  information,  or  Policy  3  Communications,  

Policy 4 Student Services , Policy 8 Finance .  

  

  

  

  

  

  

  

  

  

  

  

  

  

  

  



                                                               15  

                                            

                                          Graduate Students’ Association  

                                         Executive Duties Policy Manual  

  

