2.1 Executive Elections   2.1.1 Chief Electoral Officer (CEO) Statement of Responsibilities   2.1.1.1 The CEO’s overriding priority shall be to ensure that elections are well advertized to the student body and are fair and impartial. The CEO will do this by:   i) Collecting all nomination forms and ensuring candidates have fulfilled the requirements stated in the forms.   ii) Explaining the rules and procedures of the election to all nominees and providing a package that includes these details.   iii) Advertizing election details in accordance with Policy 3.   Communication.   2.1.1.2 The CEO shall monitor and resolve any infractions of the election policy.   2.1.1.3 The CEO shall not endorse any candidate and must remain publicly neutral.   2.1.1.4 The CEO, also the current GSA Council Chair, is appointed by the Vice President Operation and Communication.   2.1.1.5 The CEO is responsible for any and all matters relating to election campaigning expenses and disputes.   2.1.1.6 The CEO shall only make a ruling after a proper investigation has been conducted. A sanction will only be issued where the CEO has determined that a violation has occurred and has compelling evidence. The CEO shall interview any individual deemed relevant, and ensure that the offending party or parties have the opportunity to respond to any allegation made.  2.1.1.7 When a situation arises that is not explicitly considered by this consistent with its intentions.   2.1.1.8 The CEO shall, during the nomination and campaigning period, be available to receive any dispute or complaint.   2.1.1.9 The CEO shall organize and Chair a Candidates Forum to be held during Campaign week   2.1.1.10 Should it be necessary due to unforeseen circumstances to alter, extend or cancel previously set election dates, the CEO shall be empowered to do so.   2.1.1.11 The CEO shall declare any potential personal conflict of interest to GSA Course Council prior to validation day. Where a conflict of interest has been determined to exist, the CEO shall be required to appropriately alter their responsibilities, take a leave of absence or resign.   2.1.1.12 The CEO will receive an honorarium in the value of the graduate student hourly rate for each hour of work committed to the election process.   2.1.2 Elections Timeline   2.1.2.1 The Executive of the GSA shall be elected before April 15.   2.1.2.2 Nominations will be open for two weeks for all positions. Should no nominations be received, the nomination period can be extended by one week for unfilled positions. After an extended period, if no nomination is received then the Chief Electoral Officer shall refer the vacant position(s) to the next General Meeting or Course Council Meeting, whichever comes first, to fill the position(s) as follows:  i) Call for nomination to the vacant position(s) during the next general meeting of GSA Council meeting and direction from the GSA Executive or GSA Council regarding the election.   ii) If only one candidate is nominated, the candidate will present a short speech promoting themselves. GSA Council may vote by show of hands after the candidate has left the room.   iii) If two or more candidates are nominated for a given position, each candidate will present a short speech promoting themselves. After such time, GSA Council will vote to fill the vacant position. Voting will be done by secret ballot and will be counted by the GSA Council Chair, who is also the Chief Electoral Officer, and they will immediately release the results.   2.1.2.3 After nomination period has ended, and all nomination forms have been confirmed by the CEO the campaign period will begin the next day. The Campaign period will run for one week (5 business days).   2.1.2.4 The CEO will hold a Candidates Forum that is open to all GSA members.   2.1.2.5 Voting will be held at the end of the campaign period. The incumbent Vice President Operations and Communication will facilitate an online poll.   2.1.2.6 Candidates shall not engage in campaigning during the nomination period.   2.1.3 Nominations   2.1.3.1 All current members of the GSA are eligible to run for positions of the GSA Executive.   2.1.3.2 Nomination Packages are to be made available at the GSA office and on the GSA Website for the duration of the nomination period. These packages must contain the following information:   i) The position(s) to be contested for.   ii) A Nomination Form.   iii) A copy of the GSA Constitution, Bylaws and Policies.   2.1.3.3 Nomination Forms must be signed by:   i) A nominator and a seconder   ii) The nominee   iii) 5 supporting GSA members   2.1.3.4 Nomination signatures may not be collected in campus pubs, cafeterias, GSA offices, and GSA Commons.   2.1.3.5 Candidates shall take a leave of absence during the campaign period from all extracurricular activities that, in the judgement of the CEO, convey unfair advantage, or establish or imply a conflict of interest. Notices of Leave shall be provided to the CEO.   2.1.3.6 A nominee may withdraw his or her candidacy at any time before the end of the nomination period. Should a candidate decide to withdraw his or her candidacy during the campaign period, a notice of withdrawal in written form shall be given to the CEO.   2.1.4 Election Campaigning   2.1.4.1 No campaigning shall take place outside of the campaigning period.   2.1.4.2 Campaigning is defined as any activity that, in and of itself, serves to publicize or promote an individual’s candidacy in a GSA election.  2.1.4.3 Campaigning includes and is limited to the use of booked rooms for public gatherings, public appearances, emails with more than 5 recipients, distribution of posters, and websites.   2.1.4.4 The GSA will provide the copying of a maximum of fifty (50) campaign posters.   2.1.4.5 All campaign materials and promotions are subject to the approval of the CEO. A sample of all campaign materials shall be submitted to the CEO to be kept on file for the duration of the campaign. All posters must be stamped by the CEO to indicate approval.   2.1.4.6 The contents and methods of campaigning shall be above reproach. Candidates shall not misrepresent the character or policies of other candidates, nor shall they interfere in any manner with the campaign materials of other candidates. Candidates shall not make statements that they know are untrue. All campaigning is subject to the approval of the CEO.   2.1.4.7 Campaign posters shall be no larger than 11 inches by 17 inches.  There shall be a limit of fifty (50) posters approved per  team/candidate.   2.1.4.8 Should a campaign poster be torn down, the CEO may use their  discretion to approve a new poster to replace it, so long as no  more than 50 posters are on display at one time.   2.1.4.9 Posters may not be affixed to painted areas, doors, or glass.  Candidates are responsible for ensuring that campaigning  conforms to individual building policies.   2.1.4.10 The CEO will advertize and chair a Candidates Forum that is  open to all GSA members.   2.1.4.11 Candidate profiles will be posted on the GSA website.   2.1.4.12 No campaigning shall take place in a scheduled class or lab,  seminar.   2.1.4.13 No form of off-campus campaigning shall be permitted.   Candidates shall not place campaign materials on trees or utility   poles either on or off campus.   2.1.4.14 Campaign/promotional materials may not be distributed to   mailboxes on or off campus, nor shall any form of door-to-door   campaigning be permitted.   2.1.4.15 No candidate may campaign publicly inside campus pubs or  cafeterias. Campaigning shall be permitted in line-ups but shall  not occur past the point where patrons are requested to provide  identification for entrance. Campaigning in line-ups shall also be  subject to any applicable residence or university regulations.   2.1.4.16 Campaign materials shall not be distributed in campus pubs,  cafeterias, or GSA Commons.   2.1.4.17 Email addresses may be collected by candidates subject to the  approval from the student to distribute campaign information. All  email content shall be consistent with previously approved  campaign material and shall be above reproach.   2.1.4.18 At the end of the campaign period, each candidate or team of  candidates will be required to remove all campaign materials  produced on their behalf for the purposes of the election by 8:00  pm on the day preceding the first day of voting. Websites and  other online content may remain available, but may not be altered  after the 8:00 pm deadline.   2.1.4.19 No polls or surveys of public opinion regarding GSA Elections  shall be published or broadcast on the day(s) of voting.   2.1.4.20 Individuals who hold GSA Executive positions and who are  serving as campaign managers, advisors or individuals otherwise  closely associated with a team’s campaign, shall declare this to  the president and the CEO. The CEO, in consultation with the  President, may require an individual to assume either altered responsibilities or take a leave of absence, if in their judgment  conveys an unfair advantage, or establishes or implies a conflict  of interest. All leaves of absence shall last for the duration of the  campaign period.   2.1.4.21 GSA Executive members and employees shall not use any  resources of the GSA to endorse or speak against any election  candidate publicly. This includes, but is not limited to:   i) Publishing opinions using a designated GSA title.   ii) Using a GSA email account to disseminate information.   iii) Using the GSA logo on any material.    2.1.4.22 GSA Council shall be a neutral forum. No promotional materials  shall be displayed or distributed to Course Council.   2.1.4.23 Candidates are responsible for the conduct of their campaign  organization and its members. Any violation of elections policy  by said members shall be regarded as a violation by the candidate  and their nomination may be revoked at the discretion of the  CEO.   2.1.5 Election Expenses  2.1.5.1. No candidate shall use personal funds to acquire campaign  materials of any sort. Any such materials used to promote a  candidate will be considered unauthorized and such an incident  shall be remedied at the discretion of the CEO.  2.1.5.2. The GSA will cover all costs for printing up to fifty (50) posters.   2.1.6 Polling Procedures  2.1.6.1 Polling will be open to all graduate students through the PAWS  website.   2.1.6.2 Candidates will be elected if they receive the most votes.   2.1.6.3 In the case where only one nomination is received for a position, a  yes/no vote will take place. Candidates will be elected if 50%+1 of the voters are in favor.   2.1.6.4 The Candidates’ names and positions will all be displayed in the  same font and size.   2.1.6.5 A link will be provided to the candidate profile page created on  the GSA website.   2.1.6.6 Eight percent (8%) of the total student graduate body must vote  for a general election results to be legitimate. In cases where this  does not occur a new vote must be held.    2.2 Referenda   2.2.1. GSA Council   2.2.1.1 GSA Council shall ratify the dates of GSA referenda at least a  month before a referendum is held.   2.2.1.2 Signature requirements for referenda questions shall be ratified by  GSA Council prior to the commencement of the nomination  period.   2.2.1.3 GSA Council as a whole will act as a neutral body with respect to  all referendum issues.   2.2.2. Chief Returning Officer (CRO) Statement of Responsibilities   2.2.2.1 The CRO’s overriding priority shall be to ensure that referenda  are well advertized to the student body and are fair and impartial.  The CRO will do this by:   1. Collecting referenda question.  2. Advertizing referenda details in accordance with Policy 3.  Communication.   2.2.2.2 The CRO, also the current Course Council Chair, is appointed by  the Vice President Operation and Administration.   2.2.2.3 The CRO is responsible for any and all matters relating to referenda campaigning, expenses and disputes. In exercising their  duties, the CRO may consult with any other individuals deemed  relevant.   2.2.2.4 The CRO shall only make a ruling after a proper investigation has  been conducted. A sanction will only be issued where the CRO  has determined that a violation has occurred and has compelling  evidence regarding the identities of the perpetrators. The CRO  shall interview any individual deemed relevant, and ensure that  the offending party or parties have the opportunity to respond to  any allegation made.   2.2.2.5 When a situation arises that is not explicitly considered by this  document, the CRO shall interpret policy in a manner consistent  with its intentions.    2.2.2.6 The CEO shall, during the nomination and campaign period, be  available to receive any dispute or complaint.   2.2.2.7 Should it be necessary, due to unforeseen circumstances, to alter,  extend, or cancel previously set referendum dates, the CRO shall  be empowered to do so.  2.2.2.8 The CRO will receive an honorarium in the value of the graduate  student hourly rate for each hour of work committed to the  referendum process.   2.2.3. Timetable for Referenda   2.2.3.1 All referendum questions shall be held within a stated time period  once per year. All attempts shall be made to hold the referenda in  October. GSA Council at their discretion may open more than one  referendum period within an academic year. It is strongly  discouraged to open more than one referendum period unless  under extenuating circumstances. A second referendum period  can be opened with a two-thirds (2/3) majority vote by GSA  Council.  2.2.3.2 Each referendum period will be promoted through the GSA  website one month prior to the opening for nominations. A  referendum period must be held each term and the time period for  the acceptance of nominations will be set by the incumbent Vice  President Operations and Communications. If no nominations are  received no referendum will be held.   2.2.3.3 The incumbent Vice President Operations and Administration  shall issue a proclamation one month before the nomination  period outlining the following:   i) The opportunity to nominate a question for referendum.   ii) The dates and times of the nomination period.   iii) Where nomination packages can be obtained and  deposited.   iv) The dates of the vote.   v) The Executive must advertise the referendum question,  dates and polling method via all possible means of  communication, minimum the GSA website, posters,  email and PAWS announcement.   vi) The Executive must advertise the referendum question,  dates and polling method via all possible means of  communication, minimum the GSA website, posters,  email and PAWS announcement.   2.2.4. Nominations   2.2.4.1 Any GSA member can bring forward nominations of a referenda  question but must be affiliated with a ratified Academic Council.   2.2.4.2 The nomination period is purely for organizational purposes and  for collecting nomination signatures. No campaigning (as defined in Policy 2.2.5. Campaigning) shall occur during the nomination  period.   2.2.4.3 Nomination Packages are to be made available at the GSA office  on the opening day of the nomination period onwards. These  packages must contain the following information:   i) “GSA Referenda”.   ii) The formula for writing referenda questions.   iii) A Nomination Form.   iv) A copy of the constitution pointing out relevant policies  and procedures.   v) A campaign expense form.   2.2.4.4 Nomination Forms must be signed by fifty (50) current GSA  members.   2.2.4.5 Nomination signatures may not be collected in campus pubs,  cafeterias, or at any GSA common space.   2.2.4.6 The CRO shall keep available for public viewing in the GSA  Commons a list of questions approved and verified that are to  appear on the referendum. Such information will also be made  available on the GSA website at the close of the nomination  period.   2.2.4.7 An organization may withdraw its referendum question at any  time before the end of the nomination period. A notice of  withdrawal shall be given in written form to the CEO.   2.2.5. Referenda Campaigning   2.2.5.1 Campaigning shall not commence until the beginning of the  campaign period.   2.2.5.2 Campaigning is defined as any activity that, in and of itself, serves to publicize or promote an individual’s or  organization’s position in a GSA referendum.   2.2.5.3 Campaigning includes, but is not limited to, use of booked rooms  for public gatherings, public appearances, issue of policy  statements, distribution of promotional materials or information,  paid advertising in campus media, etc.   Should an event, organized prior to the nomination period for  reasons unrelated to the referendum, be scheduled to take place  during the campaign period, the organization responsible for it  can submit a request to the CRO asking that the event be  considered a non-campaign event. If the CRO determines that the  event cannot be rescheduled, the request may be granted, so long  as no mention of the campaign is made at the event.  2.2.5.4. All campaign materials and promotions are subject to the approval  of the CRO. A sample of all campaign materials shall be submitted  to the CEO to be kept on file for the duration of the campaign. All  posters must be stamped by the CEO to indicate approval.  2.2.5.5. The contents and methods of campaigning shall be above reproach.  Organizations shall not misrepresent the character or policies of  other organizations, nor shall they interfere in any manner with the  campaign materials of other candidates. Candidates shall not make  statements that they know are untrue. All campaigning is subject to  the approval of the CRO.  2.2.5.6. Campaign posters shall be no larger than 11 inches by 17 inches.  There shall be a limit of fifty (50) posters approved per  team/candidate.  2.2.5.7. Should a campaign poster be torn down, the CEO may use his/her  discretion to approve a new poster to replace it, so long as no more  than fifty (50) posters are on display at one time.  2.2.5.8. Posters may not be affixed to painted areas, doors, or glass.  Candidates are responsible for ensuring that campaigning  conforms to individual building policy.  2.2.5.9. No campaigning shall take place in a scheduled lecture or lab.  2.2.5.10. No form of off-campus campaigning shall be permitted.  Candidates shall not place campaign materials on trees or utility  poles either on or off campus.  2.2.5.11. Campaign or promotional materials may not be distributed to  mailboxes on or off campus nor shall any form of door-to-door  campaigning be permitted.  2.2.5.12. No campaigning will take place in a student residence.  2.2.5.13. No candidate may campaign publicly inside campus pubs or  cafeterias. Campaigning shall be permitted in line-ups but shall not  occur past the point where patrons are requested to provide  identification for entrance. Campaigning in line-ups shall also be  subject to any applicable residence or university regulations.  2.2.5.14. Campaign materials shall not be distributed in campus pubs,  cafeterias, or GSA Commons.   2.2.5.15 Email addresses may be collected by candidates subject to the  approval from the student to distribute campaign information. All  email content shall be consistent with previously approved  campaign material and shall be above reproach.   2.2.5.16 Each candidate or team of candidates will be required to remove  all campaign materials produced on their behalf for the purposes  of the election by 8:00 pm on the day preceding the first day of  voting. Websites and other online content may remain available,  but may not be altered after the 8:00 pm deadline.   2.2.5.17 No polls or surveys of public opinions regarding GSA Elections  shall be published or broadcast on the day(s) of voting.   2.2.5.18 Individuals who hold GSA positions or any elected leadership  position in its member association, and who are serving as  campaign managers, advisors or individuals otherwise closely  associated with a team’s campaign, shall declare this to their  supervisor and the CRO. The CRO, in consultation with the  supervisor, may require an individual to assume either altered  responsibilities or take a leave of absence, if in his/her judgment it conveys an unfair advantage, or establishes or implies a conflict  of interest. All leaves of absence shall last for the duration of the  campaign period.   2.2.5.19 GSA Executive members and employees shall not use any  resources of the GSA to endorse or speak against any election  candidate publicly. This includes, but is not limited to:   i) Publishing opinions using a designated GSA title.   ii) Using a GSA email account to disseminate information.   iii) Using the GSA logo on any material.   2.2.5.20 Course Council shall be a neutral forum. No promotional  materials shall be displayed or distributed at Course Council.   2.2.5.21 A group or party wishing to run a “No” campaign must register  with the CRO. Only one party may campaign against any  question. In the event that more than one party provides notice of  their intent to run a “No” campaign against the same question, the  CRO shall request that these parties merge to run a single  campaign. If the parties are unable to reach agreement, the CRO  shall determine which party shall run the “No” campaign. The  CRO shall rule in favor of the first party to provide written notice  of intent, unless they determine that a subsequent applicant has a  significantly greater interest in the outcome of the question, or  significantly greater willingness and ability to affect the outcome.  The CRO’s ruling in this matter is not subject to appeal. “No”  campaigns shall be provided with the same resources made  available to the group placing the question.   2.2.5.23 No member of the GSA shall be eligible to run multiple “No”  campaigns at the same time.   2.2.5.24 Campaign organizations are responsible for the conduct of their members and volunteers. Any violation of referenda policy by  said members and volunteers shall be regarded as a violation by  the campaign organization.   2.2.6. Referenda Expenses   2.2.6.1 No organization or group shall use any internal or external funds  to acquire campaign materials of any sort. Any such materials  used to promote a referendum question will be considered  unauthorized and such an incident shall be remedied at the  discretion of the CEO.   2.2.6.2 The GSA will cover all costs for printing all posters.   2.2.7. Polling Procedures   2.2.7.1 Polling will be open to all graduate students through the PAWS  website. In special circumstance where polling stations must be  used section 2.2.5 and 2.2.6 will be enforced.   2.2.7.2 A 50% + 1 majority vote binds the GSA to the commitments of  the referendum.  2.2.7.3 The quorum required for referendum results to be binding will be  no less than 8% and recommended by the Executive and subject  to debate and approval by a two-thirds (2/3) majority vote of the  GSA Council. Approval must occur at the same time as the  approval of the referendum question in accordance with the  Constitution.  2.2.7.4 In the event that a quorum condition is not approved by a two-  thirds (2/3) majority of the GSA Council, quorum shall be held at  8% of the total graduate student body.