3.1 Communications   3.1.1.1 The GSA will endeavour to engage all of its members and the university community. The Vice President Operations and Communication will oversee communication and advertising activities of the GSA.   3.1.1.2 The GSA will not publish or promote materials deemed by the Vice  President Operations and Communication to be racist, sexist, libellous or  homophobic. These terms are defined as any material which promotes a  derogatory stereotype, contains language that is insensitive to these groups,  promotes hatred or fear, makes false or misleading statements or is in  violation of libel laws of Canada.   3.1.1. GSA Logo  3.1.1.1 All advertisements about GSA events and events endorsed by the GSA  will include a GSA logo.  3.1.1.2 The GSA logo will be available on the GSA website. Only the logo  provided by the GSA will be used.  3.1.1.3 The GSA logo will not be used without the approval of GSA Staff under  the direction of the Vice President Operations and Communications.   3.1.2. Internal Communication  3.1.2.1 Clear communication within the GSA will ensure efficiency and  proficiency of its executive and staff. The GSA will document and  communicate information that will be useful to current and future executive  and staff members.   3.1.3. Communications with the Graduate Student Body   3.1.3.1 All GSA members must be informed of GSA news and events.  Important news will be advertised through e-mails to the entire student body  through the College of Graduate Studies and Research, on the GSA website,  through PAWS and through posters distributed across campus. These  announcements will include:   i) Elections.   ii) Referenda.  iii) Bursary deadlines.   iv) Orientation.   v) Major social events.   vi) Job Postings.   vii) Interdisciplinary conferences.   viii) Special and Annual General Meetings.   3.1.3.2 More casual events will be advertised through the website, emails to  GSA Councillors and posters distributed across campus.   3.1.3.3 The President will publish an annual report that will be made  available to the GSA membership and its stakeholders.   3.1.3.4 The Aboriginal Liaison will promote awareness of the Aboriginal and  Indigenous Graduate Students’ Council activities.   3.1.3.5 The GSA will consult with the University of Saskatchewan  Undergraduate Students’ Union is matters of common interest.   3.1.4. External Communication  3.1.4.1 The Vice President External shall be responsible for communication  with national and international student unions.   3.1.4.2 The Vice President Operations and Communications shall be  responsible for publications submitted to University or community  newspapers.    3.2 Website   3.2.1.1 The purpose of the GSA website is to publicize news, events,  initiatives and governing procedures for its members and the community. In every way, the website will aim to engage students and provide  transparency to the operations of the organization. Interested parties will  have the opportunity to subscribe to the website to receive e-mail updates  about GSA News and Events.   3.2.2 Website Content   The website will include:   3.2.2.1 News postings   i) All news that is pertinent to graduate students will be published on the  GSA website with news specific to the GSA will be posted at the top of  the News page.   3.2.2.2 Campaigns   i) Current initiatives will be described on the website.   3.2.2.3 GSA Commons   i) Events and programming of the GSA Commons   ii) Information about how graduate students and external parties may use  the GSA Commons for graduate student events.   3.2.2.4 Governance information   i) Outline of governing structure and governing documentation.   ii) Detailed financial records of the organization including results of  professional audits.   iii) Description of executive positions and contact information for current  executives.   iv) GSA Council, Special General and Annual General Meeting schedules  and minutes.  v) Listing of GSA Council representatives.   3.2.2.5 Resources   i) A directory of resources available to students through the GSA and  externally.   3.2.2.6 Contact information  i) Contact information for the Executive and location of the GSA.   3.2.2.7 Links to all ratified Academic Council and social groups’ websites  and their most recent year of ratification.  i) Contact information of each Academic Councillor  ii) The most recent year of ratification for each Academic Councillor.   3.2.3 Surveys   3.2.3.1 The GSA may survey its students in order to determine the needs of  its constituents. Surveys will be administered using the University of  Saskatchewan survey tool (survey.usask.ca). Surveys are preferred to be  distributed in term one whenever possible.    3.3 E-mail   3.3.1.1 GSA Executive and Staff members will have access to e-mail  addresses associated with their position. Email correspondence will be clear,  professional and always within the limitations with University of  Saskatchewan Electronic Mail Policy (available at:  http://www.usask.ca/university_secretary/policies/operations/4_42.php).   3.3.1.2 The GSA executive will revoke the e-mail privileges of any member  who is using their GSA e-mail in inappropriate ways.   3.3.1.3 E-mail will not be used to resolve conflict. This may be used as a tool  to schedule a meeting to solve conflict face to face only.  3.3.1.4 E-mails to the entire student body will be vetted through the Vice  President Operations and Administration and must be sent through the  College of Graduate Studies and Research.  3.3.1.5 The outgoing Executive shall make themselves available to aid the  incoming Executive for the first month of the new term. If the outgoing or  incoming Executive is not available for at least one transition meeting, the  honorarium of that Executive shall be waived for their last or first month,  respectively.   3.3.1.6 Auto responses will be set when staff and Executives are away. Auto  responses will indicate the date of return and who to contact form more help  in the interim.   3.3.1.7 In the event of long absences, emails will be forwarded to another  Vice President to ensure that immediate issues are dealt with.   3.4 Transition Manuals   3.4.1.1 In order to ensure a smooth transition between executives and uphold  constitutional memory, incoming executive members will receive a  transition manual outlining the operational details about the requirements of  their role. Each executive member will maintain and update this transition  manual throughout their term.   3.4.1.2 At a minimum, the transition manual will include:   i) A copy of the constitution, bylaws and policy manuals, highlighting all  sections that directly apply to each individual position.   ii) Detailed information about the progress of current initiatives and  promises made to committees, council and the student body.   iii) Contact information and resources available to each executive position.   iv) Contact and scheduling information for the committees that the position  has served on.   v) A list of recommended improvements for the role.  3.4.1.3 Before relinquishing office all Executives shall ensure that their  incumbent has the tools that they need to fulfill the mandate of the position.  The outgoing executive shall answer any questions that the incoming  executive may have and will notify them of duties that may not be  outwardly obvious.   3.4.1.4 Wherever possible, the incoming executive shall shadow the outgoing  executive for the last few weeks of April upon election.  3.4.1.5 The outgoing Executive shall make themselves available to aid the  incoming Executive for the first month of the new term. If the outgoing or  incoming Executive is not available for at least one transition meeting the  honoraria of that Executive member shall be waived for their last or first  month, respectively.   3.5 Constitution   3.5.1.1 The Vice President External shall perpetually review the constitution,   policies and bylaws to ensure that they remain accurate, relevant and   current.   3.5.1.2 In small housekeeping changes may be brought to GSA Council for   approval.   3.5.1.3 Major constitutional revisions will be proposed by a Constitutional   Revisions Sub-committee, chaired by the Vice President External Affairs.   Major revisions will be read no less than two times.   3.5.1.4 No constitutional amendments will be officially approved during a   referenda or election, though amendments may be publicized for open   review at that time.  3.6 GSA Student Handbook    3.6.1.1. The GSA shall publish a handbook for graduate students.   3.6.1.2. The GSA Handbook will contain information about the organization and   how to get involved.   3.6.1.3. The GSA Handbook will also contain a day planner.   3.6.1.4. The Handbook will be compiled by the Vice President External with the   help of the Office Administrator.   3.7 Confidentiality Policy   The GSA often deals with topics that are not appropriate for publication.   Confidential files will be clearly labeled as such and will be signed and dated by   involved parties. Unless otherwise specified, confidential files will be kept for an   indefinite period. There are a few different ways that the GSA will handle these   issues:   3.7.1 In Camera meeting minutes   3.7.1. GSA Executives, GSA Council and sub-committees may keep confidential   any discussion which the committee feels is sensitive.   3.7.2. In place of the private discussion, the minutes will read “In-Camera”.   3.7.3. A record of the discussion will be made and placed in an In-Camera file.   3.7.4. The In-Camera file will only be accessible by members of the appropriate   committee and the Executive.   3.7.5. All committee members present should sign and acknowledge In-Camera   Minutes.  3.7.2.1. There may be situations in which the speaker has information but feels   that such comments should be kept off the record.   3.7.2.2. The speaker will indicate if he/she wishes their comments to be recorded,   or kept off the record.   3.7.2.3. If the chair decides that such information has merit, then the chair may   overrule the speaker, and said comments will be placed into the minutes.    3.7.3 Student Advocacy   3.7.3.1. The GSA will uphold the confidentiality of individual students inquiring   about academic or employment related grievances.   3.7.3.2. Files kept on current advocacy cases will be available to the Vice   President(s) dealing with the case and the student(s) they are advocating   for with the exception of third party information that is promised to   remain confidential.   3.7.4 Human Resources Information   3.7.4.1. As an employer, the GSA will uphold the confidentiality of its   interviewees and employees.   3.7.4.2. Interview information, including resumes, interview process, selection   criteria and interviewer notes will be kept on file for 2 years.   3.7.4.3. Performance appraisals will be kept on file for 2 years.   3.7.4.4. These files will be available to the President and Vice President   Operations and Communications and other executives only when   appropriate.   3.7.5 Bursary Applications   3.7.5.1. All bursary applications will remain confidential and will be filed for 1 year.   3.7.6 Executive Members   3.7.6.1. Personal information and details about private issues of an individual   executive member will remain confidential.   3.7.6.2. Election nomination forms will be filed for 2 years and will remain   confidential.    3.7.7 GSA Council Members   3.7.7.1 Personal information of course council members will remain confidential.   Records of GSA council attendance and participation will be stored for 2   years.   3.7.7.2 The GSA will publish, on the GSA website the contact information of   GSA councillors.   3.7.8 Insurance   3.7.8.1. The Vice President Student Affairs can keep a file regarding individual   student sensitive insurance issues.   3.7.8.2. The Insurance files will be accessible by the Vice President Student   Affairs and the President, or designate.