----------------------- Page 1-----------------------

  
  
  
  
  
  
  
  
  
                                           University of Saskatchewan  
  
                                   Graduate Students’ Association  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
                                                      Policy Manual  
  
                                                 4. Student Services  
  
  
  
  
  
  
  
Created April 13, 2010  
  
Last Updated: April 26, 2010  

                                                                    1  

                                   Graduate Students’ Association  

                                        Student Services Manual  

  

----------------------- Page 2-----------------------

                                             Table of Contents  
                                               
  4.1      Bursaries ............................................................................................... 3  

       4.1.2.     Eligibility ....................................................................................... 3  

       4.1.3.     Bursary Fund Amount and Distribution ........................................ 3  

       4.1.4.     Application Procedure ................................................................... 3  

       4.1.5.     Bursary Selection Process ............................................................. 4  

       4.1.6.     Awarding Bursaries ....................................................................... 5  

  4.2      Health and Dental Insurance ................................................................ 5  

  4.3      Social Groups ....................................................................................... 5  

  4.4      Student Advocacy ................................................................................. 7  

  4.5      Orientation ............................................................................................ 8  

                                               

                                                               2  

                                   Graduate Students’ Association  

                                        Student Services Manual  

  

----------------------- Page 3-----------------------

  
  
                                       4.1      Bursaries   

4.1.1.1        The  Bursary  Fund  will  provide  assistance  to  those  graduate  
               students   who   are   ineligible   for   other   awards   (e.g.   NSERC,  
               SSHRC etc.), who demonstrate difficulties in acquiring funding,  
               community involvement and good academic standing.   

4.1.1.2        Bursary   documents,   including   applications   will   be   kept   in  
               confidential files, in accordance with Policy 3.7 Confidentiality.   

  

4.1.2. Eligibility  

4.1.2.1.     Applicants   must   be   registered   as   a   graduate   student   at   the  
             University of Saskatchewan in the term of award.   

4.1.2.2.     Students are only eligible to receive bursaries once in a year (once  
             in every three terms).   

4.1.2.3.     Current executive are not eligible for GSA Bursaries.   

  

4.1.3. Bursary Fund Amount and Distribution  

4.1.3.1.     The bursary fund shall be no less than $3 000 for each term. This  
             will come from the GSA’s operational budget, donations and fund  
             raising events.   

4.1.3.2.     The bursary fund will be distributed evenly between four bursary  
             recipients.  

4.1.3.3.     The  bursary  selection  committee  may  chose  to  re-distribute  the  
             allocation of the bursary fund in special circumstances.   

4.1.4. Application Procedure  

4.1.4.1        Applications will require the submission of:   

         i)       A one page cover letter written by the applicant, outlining their  
                  situation and why they are deserving of the bursary.   

         ii)      A  completed  bursary  application  form  (available  at  the  GSA  
                  office and on the website).   
                                                  3  

                                   Graduate Students’ Association  

                                        Student Services Manual  

  

----------------------- Page 4-----------------------

  

         iii)    One  letter of recommendation  from  a  faculty  member  in  their  
                 department.   

4.1.4.2       Applications will be accepted in hard copy only.   

4.1.4.3       Application deadlines are as follows:   

         i)      Fall term: Mid October.  

         ii)     Winter term: Mid February.   

         iii)    Summer term: Mid June.  

  

4.1.5. Bursary Selection Process  

4.1.5.1       The      Graduate        Students'      Association         Bursaries       Selection  
              Committee         will    be    chaired      by    the     VP     Operations       and  
              Administration and will include the Vice President Finance, and a  
              minimum of two (2) Course Councilors. Bursary applicants may  
              not sit on the committee. A new bursary selection committee will  
              be convened for each term. There will be only one representative  
              from any given department.   

4.1.5.2       Although        all   graduate      students      are    encouraged        to   apply,  
              preference will be given to students in the following situations:   

         i)      Students that are ineligible for large scholarships.  

         ii)     Part time students.  

         iii)    Senior  students  who  have  exhausted  the  funding  for  their  
                 program.  

         iv)     Students in need of child care services.  

         v)      Students who have   demonstrated financial need, good  
         community involvement and academic performance.  

  

4.1.5.3       The  Bursary  Selection  Committee  shall  use  a  Bursary  Selection  
              Rubric  that  considers  academics,  dependent  children,  whether  
              they are international students or not, if they have a disability and  

                                                 4  

                                   Graduate Students’ Association  

                                        Student Services Manual  

  

----------------------- Page 5-----------------------

               their  income  to  rank  applicants.  The  top  ranking  applicants  will  
               be awarded equal amounts.   

4.1.6. Awarding Bursaries  

  4.1.6.1      Bursary  recipients  will  be  notified  within  two  weeks  of  the  
               deadline.   

  4.1.6.2      The  GSA  may  announce  that  bursaries  have  been  awarded,  but  
               will not release names of recipients.   

  

                      4.2      Health and Dental Insurance   

  

  4.2.1.1      The   Vice   President   External   Affairs   will   act   as   the   liaison  
               between  the  health  and  dental  insurance  provider  and  course  
               council and will report on information pertaining to the insurance  
               plan.   

  4.2.1.2      All GSA members will have access to health and dental insurance  
               through the GSA under terms outlined by the insurance provider.   

  4.2.1.3      Course  Council  will  decide  on  the  health  and  dental  insurance  
               provider and fees by a two-thirds (2/3) majority vote.   

  4.2.1.4      There shall be a health and dental committee chaired by the VP  
               External  Affairs  consisting  of  at  least  one  additional  Executive  
               member and at least one Academic Councilor who shall discuss  
               health  and  dental  changes  and  make  a  recommendation  to  GSA  
               Council.   

  

                                   4.3     Social Groups  

  

  4.3.1.1      The   Vice   President   Student   Affairs   will   be   responsible   for  
               overseeing the ratification of Social Groups  

  4.3.1.2      The purpose of a Social Groups Policy is to provide for the social  
               and  academic  needs  of  GSA  members.  With  the  provision  for  
               funding  in the  operating  budget  of  the  GSA  support  is  given  to  
                                                  5  

                                   Graduate Students’ Association  

                                        Student Services Manual  

  

----------------------- Page 6-----------------------

              groups who:   

        i)      Have a minimum of 75% of its total membership that are GSA  
                members   

        ii)     Have members from more than one Academic Council.   

4.3.1.3       Prospective      campus       clubs    must     complete      and     submit     an  
              application for ratification along with a copy of their constitution  
              no later than September 30.   

4.3.1.4       Social Group status will be effective from September 1 to August  
              31.   

4.3.1.5       Social Group must reapply for campus club status each academic  
              year.   

4.3.1.6       Social Group will be ratified by a two-thirds (2/3) majority vote  
              of GSA Council.   

4.3.1.7       The  constitution  of  GSA  Social  Groups  must  be  in  accordance  
              with Robert’s Rules of Order.   

4.3.1.8       A Social Group must:   

        i)      Exist for the betterment of its members.   

        ii)     Use membership fees and money garnered for the objectives  
                outlined in the constitution of that club.   

        iii)    Elect its executive in a democratic fashion.   

        iv)     Hold public meetings.   

        v)      Make       its   governing        documents        public     to    its  
                membership and the GSA.   

        vi)     Not exist for the purpose of discrimination or harassment of any  
                group.   

        vii)    Not exist for the financial betterment of its members.   

        viii)   Not restrict membership on a basis of sex, race, gender identity  
                etc., unless approved by GSA Council.   

4.3.1.9       A  Social  Group  not  operating  in  accordance  with  the  Social  
              Groups  Policy  may  have  its  membership  as  a  campus  club  

                                               6  

                                   Graduate Students’ Association  

                                        Student Services Manual  

  

----------------------- Page 7-----------------------

              revoked,  subject  to  a  two  thirds  (2/3)  majority  vote  of  GSA  
              Council.   

4.3.1.10      In the event the application for ratification is rejected, the  Social  
              Group may launch an appeal to GSA Course Council by notifying  
              the Vice President Student Affairs in writing.   

4.3.1.11      Ratified Social Groups may have the privilege of:   

         i)      Access  to  the  GSA  Commons  and  its  facilities  in  accordance  
                 with Policy 6. GSA Commons.   

         ii)     Applying to the GSA for funding grants.  

         iii)    Advertizing news and events through the GSA with the  
                 approval of the Vice President Operations and Administration  
                 in accordance with Policy 3.Communications.   

4.3.1.12      Social  Groups  are  eligible  for  funding  according  to  Policy  8.4  
              Social Groups Funding.   

4.3.1.13      The  GSA  will  uphold  the  confidentiality  of  individuals  in  the  
              Social Group according to the Policy 3.7 Confidentiality.   

  

                              4.4      Student Advocacy   

4.4.1.1       Students  will  be  able  to  approach  any  GSA  staff  or  executive  
              member  with  a  sensitive  question  without  fear  of  judgment,  
              harassment or discrimination.   

4.4.1.2       With  the  exception  of  imminent  danger  to  the  individual  or  
              individuals  in  their  surrounding  or  abuse,  student  inquiries  will  
              remain  confidential  at  the  request  of  the  student  in  accordance  
              with the Confidentiality Policy.   

4.4.1.3       The GSA will not assume the role of a counselling service, social  
              services     or   disciplinarian,   but       will    work     with    students     to  
              overcome academic and non-academic issues that they are facing.   

4.4.1.4       The   GSA   Executive   and   Staff   will   have   knowledge   of  the  
              resources  available  to  students  and  to  the  GSA  in  its  role  as  a  
              student advocate and will refer students when necessary.   

                                                 7  

                                   Graduate Students’ Association  

                                        Student Services Manual  

  

----------------------- Page 8-----------------------

   4.4.1.5     The Vice President Student Affairs will act as an advocate in non  
               academic grievances.   

   4.4.1.6     The Vice President Academic will act as an advocate in academic  
               grievances.   

  

                                        4.5      Orientation   

   4.5.1.1     The  Vice  President  Student  Affairs  will  coordinate  with  the  
               University in its efforts to orient incoming graduate students.   

   4.5.1.2     The Aboriginal and Indigenous  Student Liaison will contribute to  
               the orientation of indigenous graduate students.   

                                                     8  

                                   Graduate Students’ Association  

                                        Student Services Manual  

  
