5.1 Meetings   5.1.1.1 The following procedures shall apply to GSA Council, Special  General and Annual General Meetings.    5.1.2 Scheduling, Notice and Minutes   5.1.2.1 GSA Council will meet once in the spring and summer term (May –  August) and monthly over the fall and winter terms (September –  April).   5.1.2.2 Annual General Meetings will be held in April in conjunction with a  GSA Council Meeting.   5.1.2.3 Special General Meetings will be held only under circumstances  outlined in Section 6 of the Constitution.   5.1.2.4 The meeting schedule will be posted on the GSA website.  Notification of changes to the meeting schedule will be given by  email a minimum of two weeks in advance for GSA Council  Meetings and one month for Annual General Meetings.  5.1.2.5 A draft agenda and call for additional agenda items will be sent to  GSA councillors by email at minimum five days before a council  meeting. The final draft shall be released by email and on the  website three days before the council meeting.  5.1.2.6 A draft agenda and call for additional agenda items should be  released to GSA Councillors by email five (5) business days before  a Council Meeting. The final draft shall be released by email and on  the GSA website three (3) days before the Council Meeting.   5.1.2.7 An information package containing the agenda, previous meeting  minutes, reports from all executive members and pertinent  appendices will be available to GSA Council members by email and  on the GSA website no later than three days before GSA Council  Meetings and one week before Annual General Meetings.   5.1.2.8 In the case where not all reports are received, what is available will be circulates. In the place of the missing report will be a notice  indicating that the report will be present at the Meeting.   5.1.2.9 The agenda will follow Policy 5.1.4 Meeting Procedure .   5.1.2.10 The agenda will be set by the Executive.  5.1.2.11 Academic Councillors may add points of information or motions to  agenda by contacting the Vice President Operations and  Communication no later than one week before GSA Council  Meetings and one month before Annual General Meetings.   5.1.2.12 Full minutes of Course Council and Annual General Meetings shall  be recorded and publicized by the Vice President Operations and  Communication. Meeting minutes will be publicized on the GSA  website no later than two weeks after approval. In Camera  discussions and confidential information will be handled according  to Policy 3.7 Confidentiality.    5.1.3 Duties of GSA Council Chair   5.1.3.1 The GSA Council Chair will be appointed by the Vice President  Operations and Administration and ratified by GSA council for the  term of May 1 to April 30.   5.1.3.2 The GSA Council Chair shall not vote or participate in debate.   5.1.3.3 In the event of a tie vote, the Chair shall cast the deciding vote on  the motion.   5.1.3.4 The suspension of any rule of order may be affected without notice   by the Speaker, for the duration of the meeting, if fewer than three   members object.   5.1.3.5 The Course Council Chair will receive an honorarium in the value   of the graduate student hourly rate for each hour of meeting chaired,   including a maximum of two hours total prep time for each GSA Council meeting, and a maximum of three hours of total prep time   for General meetings.   5.1.3.6 The GSA Council Chair will receive an honoraria in the value of the   grad student hourly rate for each hour meeting chaired.   5.1.3.7 In the absence of the appointed chair, the Vice President Operations  and Administration will suggest an alternate to be ratified on the  floor of the meeting at hand.   5.1.3.8 The Chair of GSA Council Meetings shall:   i) Have an understanding of the policies and procedures of GSA  Council Meetings and the GSA Governing mechanisms.   ii) Use Roberts Rules of Order to guide points of order not covered in  the GSA Policies.   iii) Preside at all GSA Council Meetings and shall preserve order and  decorum.   iv) If a request for explanation of a point of order, of practice, or of a  particular ruling, is made, the Speaker shall state the rules of  authority applicable to the case.   v) Shall not permit debate on any rulings.   vi) The Chair, after having called the attention of the meeting to the  conduct of a member who persists in irrelevance or repetition, may  direct that member to discontinue his or her speech.   vii) Grant speaking rights to non-ratified guests at meetings.   5.1.4 Meeting Operations   5.1.4.1 Call to order:   i) A motion will indicate the commencement of the meeting.   5.1.4.2 Approval of the Agenda  i) Members will vote to ratify the agenda as circulated or to accept it  pending changes.   5.1.4.3 Approval of the Minutes   i) Members will vote to accept the minutes from previous Course  Council and Annual General Meetings or accept pending revisions.  ii) Upon approval of the Minutes the Chair and Vice President  Operations and Communications shall sign and date a hardcopy.  This copy should be made available for audit if and when required.   5.1.4.4 Ratification of GSA Councilors   i) Members will vote to ratify Academic councilors who have  submitted an Academic council ratification form.   5.1.4.5 Invited Guests   i) Often, non-graduate students attend course council meetings to  report or seek feedback on matters that pertain to graduate  students. These may include reports from Student Care or the  university administration. These presentations, including  discussion, will be limited to a maximum of twenty (20) minutes if  possible.   5.1.4.6 Executive and Operations Reports   i) A report from the GSA staff and all Executive members will be  presented to the graduate student body on the activities of their  portfolio. A written report will be circulated with the agenda,  whether or not the executive member is present. The Vice  President Operations and Communication will present the staff  report in the absence of a staff member. Following each report,  council will have the opportunity to ask questions, provide  feedback or discuss points raised in the report.   5.1.4.7 New Business    i) Motions will be their own agenda item and in most cases will be accompanied by an appendix with rationale and background  information.   5.2 Executive Meetings Policy   5.2.1.1 The GSA Executive shall schedule meetings once per month  through the months of May to August and twice per month through  the months of September to April. Meetings may be cancelled at the  discretion of the executive.   5.2.1.2 Each executive member must attend 75% of the Executive  meetings. The Executive may allow more absences at their  discretion in extenuating circumstances.   5.2.1.3 Meeting minutes will be recorded and published though the GSA  website.   5.2.1.4 Some discussions may not be published according to Policy 3.7  Confidentiality. 