----------------------- Page 1-----------------------

  
  
  
  
  
  
  
  
  
                                           University of Saskatchewan  
  
                                    Graduate Students’ Association  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
  
                                                    Policy Manual  
  
                                                 6. GSA Commons  
  
  
  
  
  
  
  
Created April 13, 2010  
  
Last Updated: April 26, 2010  

                                                                      1  
                                               
                                             Graduate Students’ Association  
                                             GSA Commons Policy Manual  
  

----------------------- Page 2-----------------------

                                                Table of Contents  
                                                  
  
6.1         Graduate Students’ Association Commons .......................................... 3  

    6.1.2.         Duties of Commons Coordinators ................................................. 4  

    6.1.3.         Duties of the GSA Office Manager ............................................... 5  

6.2         Bookings ............................................................................................... 6  

    6.2.2          Terms of Use.................................................................................. 8  

    6.2.3          Cost of Use .................................................................................... 8  

    6.2.4          Alcohol Use and Provision ............................................................ 9  

    6.2.5          BBQ Use ...................................................................................... 10  

6.3        Art in the GSA Commons .................................................................. 11  
                                               
                                               
                                               
                                               
                                               
                                               
                                               
                                               
                                               
                                               
                                               
                                               
                                               
                                               
                                               
                                               
                                               
                                               
                                               
                                               
                                               
                                               
                                               
                                               
                                               
                                               
                                               
                                               
                                               
                                               
                                               
                                               
                                               
                                               
                                                                      2  
                                               
                                             Graduate Students’ Association  
                                              GSA Commons Policy Manual  
  

----------------------- Page 3-----------------------

        6.1      Graduate Students’ Association Commons   

  

6.1.1.1   The  GSA  Commons  is  located  at  1337,  College  Dr.  Saskatoon,  
           Saskatchewan. The phone number (306) 966-8471 will be answered  
           when  the  GSA  Commons  is  open.  The  second  phone  line  in  the  
           administration  office  is  (306)  966-1295,  and  the  Executive  office  
           phone number is (306) 966-2967.   

6.1.1.2   The  Vice  President  Operations  and  Communications  oversee  the  
           daily operations of the GSA Commons and will make decisions on  
           behalf of GSA Council.   

6.1.1.3   The GSA Commons will serve the needs of all graduate students. At  
           different  times  this  space  will  be  used  for  academic,  professional  
           and      personal       development          discussions,        workshops         and  
           presentations. Social activities and quiet study time will be provided  
           for.   

6.1.1.4   The  GSA  Commons  will  be  used  for  regularly  scheduled  events,  
           facilitated  through  the  GSA  staff  and  Executives.  The  GSA  will  
           work  with various student  services on campus  in order to  provide  
           educational       and     interesting      sessions.      Guest      speakers      and  
           documentaries will spark thoughtful discussion.   

6.1.1.5   With the exception of special bookings, the GSA Commons is open  
           to  all  graduate  students,  subject  to  the  hours  set  by  the  Vice  
           President  Operations  and  Communication.  Graduate  students  may  
           convene at the commons, but must allow other students to remain in  
           the space, unless a booking has been made.   

6.1.1.6   Students  and  visitors  of  the  GSA  commons  will  be  treated  with  
           respect, just as the staff and  Executive  are to be treated. GSA Staff  
           will assist when possible, and refer students to other services where  
           necessary.   

6.1.1.7   The  GSA  Commons  will  be  the  home  for  most  GSA  Council,  
           Special and Annual General Meetings and smaller meetings, such as  
           Executive  and  sub  committee  meetings.  Smaller  meetings  will  be  
           held in the Executive office, if an Executive member is present.   

  

                                                  3  
                                  
                                Graduate Students’ Association  
                                GSA Commons Policy Manual  
  

----------------------- Page 4-----------------------

6.1.1.8   The GSA Commons is well equipped with audio / visual equipment.  
             This equipment is to be handled carefully. During daily operations,  
             GSA Staff members will oversee the use of the sound system. For  
             events,  GSA  Staff  will  ensure  that  users  know  how  to  use  the  
             audio/visual equipment properly.   

6.1.1.9   The rated capacity of the GSA Commons is 99 persons at one time.   

  

                          6.1.2. Duties of Commons Coordinators  

  

6.1.2.1   GSA Commons Coordinators shall:   

  

         i)        Be  employed  in  accordance  with  Policy  7.  Employees  and  
                   Volunteers,   the          University        of    Saskatchewan           Policies       and  
                   Saskatchewan Labour laws.   

  

         ii)       Be  under  the  direction  of  the  Vice  President  Operations  and  
                   Communication.   

  

6.1.2.2   The duties of GSA Commons Coordinators shall include but are not  
             limited to:   

  

         i)        Be responsible for administrative details of the GSA Commons.   

  

         ii)       Will act as a receptionist during daily operations.   

  

         iii)      Will coordinate workshops and discussions hosted by the GSA  
                   in conjunction with other student services on campus.   

  

         iv)       Will coordinate social events that will engage the student body.   

  

                                                        4  
                                       
                                     Graduate Students’ Association  
                                     GSA Commons Policy Manual  
  

----------------------- Page 5-----------------------

         v)        Will advertize GSA events by e-mail, on the GSA website and  
                   through posters in accordance with Policy 3. Communication.   

  

         vi)       Will coordinate bookings of the GSA Commons.   

  

         vii)      Commons coordinators will not act as staff at third party events  
                   booked at the GSA Commons. Their role is only to help with  
                   using the space.   

  

         viii)     Oversee  the  selection  and  installation  of  artwork  in  the  GSA  
                   Commons.   

  

         ix)       Be assigned duties that will assist all Executive members, under  
                   the     discretion        of     the     Vice       President        Operations          and  
                   Communication.   

  

                          6.1.3. Duties of the GSA Office Manager  

  

6.1.3.1   The  GSA Office Manager shall:   

  

         i)        Be  employed  in  accordance  with  Policy  7.  Employees  and  
                   Volunteers,   the          University        of    Saskatchewan           Policies       and  
                   Saskatchewan Labor laws.   

  

         ii)       Be  under  the  direction  of  the  Vice  President  Operations  and  
                   Communication.   

  

6.1.3.2   The  duties  of  the    GSA  Office  Manager  shall  include  but  are  not  
             limited to:   

  

                                                         5  
                                       
                                     Graduate Students’ Association  
                                     GSA Commons Policy Manual  
  

----------------------- Page 6-----------------------

         i)       Be responsible for administrative details of the GSA Executive.   

  

         ii)      Will act as a receptionist during daily operations.   

  

         iii)     Refer   students         to   Executive        members        and     University       of  
                  Saskatchewan when appropriate.   

  

         iv)      Schedule appointments for the GSA Executive.   

  

         v)       Assist  the  Vice  President  Operations  and  Administration  with  
                  duties related to Policy 3.  Communications.   

         vi)      Organize  the  annual  GSA  promotional  materials  under  the  
                  direction  of the  Vice President  External  Affairs  in accordance  
                  with Policy 3. Communications  

  

         vii)     Be assigned duties that will assist all Executive members, under  
                  the     discretion       of     the    Vice       President       Operations         and  
                  Communication.   

                                        6.2       Bookings   

  

6.2.1.1  All  graduate  students  may  use  the  GSA  Commons  for  graduate  
            student events. This may include (but is not limited to) departmental  
            social      gatherings,        banquets,        pot     lucks,      lectures,      defenses,  
            conferences,        meetings,        etc.   Ideally      booking       will    not    disrupt  
            regularly scheduled commons programming, but exceptions may be  
            made.   

6.2.1.2   The  Commons  Coordinators  are  responsible  for  facilitating  and  
            supervising graduate student events under the direction of the Vice  
            President Operations and Communication.  

  

6.2.1.3   The  GSA,  at  the  direction  of  the  Vice  President  Operations  and  

                                                      6  
                                     
                                   Graduate Students’ Association  
                                   GSA Commons Policy Manual  
  

----------------------- Page 7-----------------------

             Communication reserves the right to deny use to groups that cannot  
             provide   timely,   detailed   information   about   the   event,   or   have  
             misused the GSA Commons in the past.   

  

6.2.1.4   The  GSA  insurance  policy  covers  all  events  held  at  the  GSA  
             Commons.   

  

6.2.1.5   Groups   using   the   GSA   Commons   will   be   required   to   sign  
             agreements in order to use the space and its equipment.   

  

6.2.1.6  All events hosted at the GSA Commons are endorsed by the GSA.  
             As  such, the GSA logo will be used in all advertizing of the event,  
             in accordance with Policy 3.1.1 GSA Logo.   

  

6.2.1.7   The  GSA  Commons  will  be  used  for  activities  in  the  following  
             order of priority:   

  

     i)       GSA programming including GSA Council Meetings.   

  

     ii)      GSA special events.   

  

     iii)     GSA Council public events (eg. Lectures invited and organized by  
              GSA Council members).  

  

     iv)      GSA Council private events (eg. Departmental social events) .   

  

     v)       Graduate student events.   

  

     vi)      Other events.   

  

                                                         7  
                                       
                                     Graduate Students’ Association  
                                     GSA Commons Policy Manual  
  

----------------------- Page 8-----------------------

6.2.1.8   GSA  ratified  groups  may  book  the  GSA  Commons  at  no  charge  
            during regular Commons hours, and then will be charged an hourly  
            rate   based   on   the   GSA   Commons   Booking   Package   and   in  
            agreement with the VP Operations & Communications.  

6.2.1.9   External parties may book the GSA Commons at the discretion of  
            the   VP   Operations   &   Communications.   These  groups   will  be  
            required to provide a damage deposit and pay an hourly rate based  
            on the GSA Commons Booking Package and in agreement with the  
            VP Operations & Communication.  

  

         6.2.2  Terms of Use   

  

6.2.2.1   The GSA Commons is to be used for events organized by graduate  
            students for graduate students. Others may be invited to attend.   

  

6.2.2.2   The GSA Commons are to be left in the physical state that it was in  
            before the event. Student groups will be charged for time taken to  
            clean up after events and to repair or replace damaged items.   

  

6.2.2.3   The  GSA  staff  or  Executive  members  staffing  events  are  not  
            responsible  for  coordinating  events  or  cleaning  up  after  events.  
            They are there to help with operations of the commons (eg. showing  
            users how to operate equipment).   

  

6.2.2.4   GSA  staff is responsible for ensuring that the commons is cared for  
            appropriately by users.  

  

         6.2.3  Cost of Use   

  

6.2.3.1   There  will be no charge during  regular  operating  hours  for use  of  
            the  GSA  Commons  by  GSA  Members  and  ratified  Councils  and  
            Social Groups as defined in the  Constitution  and Policy 4. Student  

                                                      8  
                                     
                                   Graduate Students’ Association  
                                   GSA Commons Policy Manual  
  

----------------------- Page 9-----------------------

            Services.  

6.2.3.2   Charges may apply to special requests.  

6.2.3.3   There will be a charge to refill propane cylinders after use of GSA  
            BBQs.   

6.2.3.4   Charges will apply if the damage is incurred.  

6.2.3.5   Charges  will apply if  the  cleanup checklist in  the  GSA  Commons  
            Rental   Agreement   is   not   completed   and   initialed   by   a   GSA  
            Commons Coordinator.  

6.2.3.6   External parties may book the GSA Commons at the discretion of  
            the Vice President Operations and Communications. These groups  
            will be required to provide a damage deposit and pay an hourly rate  
            based  on the  GSA Commons  Rental  Agreement  and in agreement  
            with the Vice President Operations and Communications.  

6.2.3.7  Non-graduate  student  groups  may  be  charged  an  hourly  rate  for  
            rental of the space, use of BBQs, provision of coffee, etc. This rate  
            will  be  agreed  upon  in  the  GSA  Commons  Rental  Agreement  
            administered by the Vice President Operations and Communications  
            and the GSA Office Manager.  

  

         6.2.4  Alcohol Use and Provision   

  

6.2.4.1   Groups serving alcohol are responsible for:   

  

    i)       Obtaining any liquor permits.  

  

    ii)      Booking the GSA Commons, subject to approval by the Commons  
             Coordinator(s).  

  

    iii)     Ensuring  that  all  university  and  provincial  liquor  regulations  are  
             abided by.  

  

                                                     9  
                                    
                                  Graduate Students’ Association  
                                  GSA Commons Policy Manual  
  

----------------------- Page 10-----------------------

    iv)       Providing any necessary security and bar-tending staff.  

  

    v)        Leaving  the  GSA  Commons  in  a  clean  and  orderly  condition  as  
              required by the Commons Rental Agreement.  

  

6.2.4.2   The  GSA  may  provide  liquor  for  use  at  private  events.  The  GSA  
            will supply only what it  has  on hand,  unless special  arrangements  
            have been made. The GSA will not purchase liquor  for individual  
            events.   

6.2.4.3   Liquor provided by the GSA will be sold ratified groups at cost. The  
            GSA  staff  will  take  stock  of  liquor  before  and  after  events.  The  
            GSA may be reimbursed by cash or  cheque at the end of the event,  
            unless other arrangements have been made.  
  
6.2.4.4   Events with alcohol will be coordinated by a minimum of  two (2)  
            sober people per fifty (50) attendees.   
  
6.2.4.5  Any Groups using alcohol at the GSA Commons are responsible for  
            policing  the  behavior  of  its  attendees.  The  GSA  Staff  are  only  
            responsible for asking the event coordinator to police the actions of  
            its members and ultimately asking the group to leave if the situation  
            escalates.   
  
  
         6.2.5  BBQ Use   
  
6.2.5.1   The  GSA  owns  two  commercial  BBQs  that  may  be  used  by  
            graduate student groups.   
  
6.2.5.2   BBQ          Rental      must       be    coordinated         through        the    Commons  
            Coordinators in advance of the event.   
  
6.2.5.3   Graduate student groups will cover the cost of propane, but will not  
            be charged for the use of the BBQs themselves.   
  
6.2.5.4   BBQs are to be left clean and functioning. Charges will apply if the  
            GSA   has   to   clean   up   the                        BBQs.   
                                                       10  
                                     
                                   Graduate Students’ Association  
                                    GSA Commons Policy Manual  
  

----------------------- Page 11-----------------------

                         6.3      Art in the GSA Commons   
  
6.3.1.1   The GSA will display artwork by graduate students in the interest of  
            supporting and showcasing the talents of our graduate students.   
  
6.3.1.2   The GSA will display the art of Master of Fine Arts (MFA) students  
            within  the  common  area  of  the  building.  Diversity  and  variety  in  
            make, medium and subject matter are the priorities when selecting  
            artwork  for  the  GSA  Commons.  The  MFA  students  will  display  
            work  with  subject  matter  and  themes  that  have  been  approved  by  
            their  advisors,  the  Department  of  Art  and  Art  History  and  the  
            University of Saskatchewan; the GSA believes that it is important  
            not to further censor the subject matter in their selections of art for  
            the space.   
  
6.3.1.3  Art   selection   and   installation   will   be  coordinated   through   the  
            Commons  Coordinators  under  the  direction  of  the  Vice  President  
            Operations and Communication.   

                                                      11  
                                     
                                   Graduate Students’ Association  
                                   GSA Commons Policy Manual  
  
