7.1. Harassment and Discrimination   7.1.1.1 The GSA seeks to prevent harassment and discrimination by  educating members of the student community as to what constitutes  such behavior.     7.1.1.2 The GSA will always make known that complaints from any  student, employee, volunteer or executive member of the GSA will be  investigated seriously, will be treated with respect and will remain  confidential when appropriate. The initiation, pursuit and support of a  complaint will not be an intimidating experience     7.1.1.3 The GSA recognizes that all of its members have the right to be  free from harassment and discrimination. The GSA is respectful of,  and will adhere to, the University policies and the law in their entirety.     7.1.1.4 Harassment and discrimination includes sexual harassment,  harassment based on gender, race, ethnicity, religion, creed and  sexual orientation. Such harassment and discrimination has the  purpose or effect of unreasonably interfering with an individual's or a  group's work or academic performance, or of creating an intimidating,  hostile or offensive working, living or academic environment.  Individuals or groups who are not the direct target of the conduct in  question may also suffer harassment and discrimination as the result  of being present when such conduct takes place.     7.1.1.5 The GSA encourages people who are feeling uncomfortable with a  situation to discuss the issue with someone, It is recognized that  discussing the issue does not mean that a complaint is being lodged. If  a volunteer or an employee wishes to discuss and/or lodge a complaint  of harassment or discrimination they may do so by raising the concern  with their direct supervisor, the human resources manager, (the Vice  President Operations and Administration), or the GSA President. If the concerns are not resolved through those venues, they are encouraged  to bring their concern forward to the University. Ultimately, the  complainant is free to go wherever or to whomever they feel the most  comfortable.     7.2. Hiring Practices   7.2.1. Applications     7.2.1.1 All positions under the GSA will be widely advertised.  Postings will be distributed through email, the Student Employment  and Career Center Job Posting website and on the GSA website in  accordance with Policy 3. Communications .     7.2.1.2 Applications will be accepted for a minimum of two weeks.     7.2.1.3 Applicants will be asked to submit a cover letter and resume. When  appropriate, a job application may be created for the position.     7.2.1.4 No applicant will be asked to disclose information about race,  gender identity, sexual orientation, economic status or marital status.     7.2.1.5 Applicants may be asked about their student status and expected  time to remain a student, for the purposes of scheduling and long  range planning only.     7.2.1.6 Job applications will be stored in confidential files for two years  in accordance with the Policy 3.7 Confidentiality .   7.2.2. Interviewing   7.2.2.1 Interviews will be coordinated by the Vice President  Operations and Communication or their designate.     7.2.2.2 There will be no less than two and no more than five interviewers.     7.2.2.3 Applicants will be advised of the interview time, location and  requirements no later than 24 hours before the interview.     7.2.2.4 Interviews will take place in a private room.     7.2.2.5 Each applicant will be asked the same questions. Questions  stemming from the applicant’s response will differ between applicants.     7.2.2.6 Interviewers ’ notes will be kept on file with other job search  documents for two years in accordance with Policy 3.7 Confidentiality .     7.2.2.7 Interviewees will be notified of the selection procedure and when  they can expect to be contacted.     7.2.2.8 All candidates that are interviewed will be informed weather or  not they have been awarded the position.     7.2.3. Hiring   7.2.3.1 The selection will not be based on race, gender identity,  sexual orientation, economic status or marital status.  7.2.3.2 It is not a requirement that the GSA only hire graduate students,  though they will be given preference.     7.2.3.3 New employees will be provided with a letter of offer outlining  the terms and conditions of the position including:   i) Description of duties.   ii) Work schedule.   iii) Pay rate.   iv) Supervisory structure   v) Start date.   vi) Holiday and sick leave provision.   vii) Reference to the Employment and Volunteer Policy and  their rights as an employee.  7.2.4. Equal Opportunities   7.2.4.1 It is the policy of the GSA to treat all employees and job  applicants fairly and equally regardless of their sex, sexual  orientation, marital status, race, colour, nationality, ethnic or national  origin, religion, age, disability or union membership status.     7.2.4.2 Furthermore the GSA will ensure that no requirement or  condition will be imposed without justification which could  disadvantage individuals purely on any of the above grounds.     7.2.4.3 The policy applies to recruitment and selection, terms and  conditions of employment including pay, promotion, training,  transfer and every other aspect of employment.     7.2.4.4 Any act of discrimination by the GSA or employees or any failure to  comply with the terms of the policy will result in disciplinary action.     7.2.5. Disciplinary Policy   7.2.5.1 The GSA requires good standards of conduct from its employees  along with satisfactory standards of work. The GSAs disciplinary  procedure applies to any misconduct or failure to meet the standards  of performance or attendance.     7.2.5.2 The purpose of the GSAs disciplinary procedure is to be corrective  rather than punitive and it should be recognized that the existence  of its disciplinary procedure is to help and encourage employees to  achieve and maintain acceptable standards of conduct, attendance  and job performance and to ensure consistent and fair treatment for  all employees.   7.3. Terms of Employment   7.3.1.1. The terms of employment for GSA Employees shall be determined  at a formal Executive Committee meeting and set out in writing in an  employee contract.     7.3.1.2. Changes in employment contract terms are valid only if they have  been passed and carried in the form of a motion at a formal Graduate  Students' Association Executive Committee meeting where written minutes  have been produced.     7.3.1.3. The Employee should be consulted prior to the meeting by the  entire Executive for the sole purpose of producing a statement from the  Employee which indicates if the proposed increase or decrease in terms of  employment are acceptable or unacceptable to the Employee, and that said  statement will be presented at the formal Executive meeting. Further, if  this signed statement is produced and presented at the meeting, attendance  of the Office Administrator at the formal Executive meeting is optional.     7.3.1.4. A minimum of two weeks written notice or pay in lieu of notice will  be given to the Office Administrator regarding any changes in the terms of  employment.     7.3.1.5. Performance appraisals, changes in employment contract  terms, and the preservation of a positive work environment for the  Employee are the collective responsibility of the Executive Committee.  7.4. Employee Reviews   7.4.1.1 Employees will undergo a review three months after their position  with the GSA begins and annually.     7.4.1.2 Annual reviews will be conducted in March or April.     7.4.1.3 The review will be conducted by the President and the Vice  President Operations and Administration.     7.4.1.4 Reviews will cover current and past accomplishments and challenges  and a vision of what will be done next.     7.4.1.5 The employee review will be an opportunity for the Employee  to discuss challenges with the Vice President Operations and  Administration and the President.     7.4.1.6 The review will be documented and stored in the Employee’s  confidential file.   7.5. Responsibility of Supervisory Personnel     7.5.1.1 Everyone under the GSA in leadership positions will strive  to create an environment free of harassment and discrimination for  those for whom they are responsible. Included within the ambit of that  responsibility is an awareness of what constitutes impermissible  harassment and discrimination, knowledge of the procedures that are  in place for dealing with allegations of harassment and discrimination,  and cooperation in the processing of complaints.     7.5.1.2 It also means that supervisors will not condone or turn a blind eye  to activities within their areas of responsibility which violate the  rights of students, faculty or staff, that they will ensure that all those  for whom they have responsibilities are aware that any form of  harassment and discrimination in all its manifestations is prohibited,  and that any complaints will be attended to immediately and  effectively.     7.5.1.3 Any member of the GSA may seek informal assistance or advice  from any GSA executive member in a leadership role. All such  consultations will be confidential in accordance with the Policy 3.7  Confidentiality .     7.5.1.4 All GSA members with supervisory, managerial or leadership  responsibilities have the responsibility to advise anyone whom they  believe have been harassed of their options and the assistance  available through the GSA, the University of Saskatchewan and the  Government of Saskatchewan, Campus Security or the police  department.   7.5.1.5 Such personnel may, without revealing the identity of the person  involved, also seek advice from the University of Saskatchewan as to  how to proceed in those instances where a person alleging to have  been subject to harassment or discrimination is unwilling to take the  matter to an advisor.     7.5.1.6 In the case of apparent group or systemic harassment or  discrimination, such personnel may themselves take a complaint to an  advisor on behalf of those allegedly harassed or discriminated against.   7.5.1.7. The President shall preside over the operations of direct supervisors  of GSA Staff. In the event of a concern with the direct supervisor, the  GSA President will be the next in the chain of command. 