----------------------- Page 1-----------------------

  

  

                                                          

                             University of Saskatchewan   

                         Graduate Students’ Association  

                                                          

                                                                               
                                                          

                                          Policy Manual   

                                  9. Position Statements  

                                                          

                                                          

                                                          

Created April 13, 2010  

Last Updated: April 26, 2010  

                                    Graduate Students’ Association  
                                   

                                  Position Statements Policy Manual  

                                                      9-1  

----------------------- Page 2-----------------------

                                          Table of Contents  

 8.1     Position Statements .................................................................................................. 3  

 8.2     Tuition Position Statement ....................................................................................... 3  

  

                                        Graduate Students’ Association  

                                     Position Statements Policy Manual  

                                                            9-2  

----------------------- Page 3-----------------------

                             8.1      Position Statements  

7.1.1.1 Position statements herein are binding for the GSA.  

7.1.1.2 Position statements will be included in this policy with a two-thirds (2/3) majority  
         vote at Course Council.   

7.1.1.3 Any  GSA  member  may  bring  forth  a  position  statement  for  considerations  by  
         Course Council.  

                       8.2      Tuition Position Statement  

Accepted by Course Council on February 25, 2010  

The  Graduate  Students’  Association  (GSA)  at  the  University  of  Saskatchewan  cannot  
support the notion of any future tuition increases for graduate students at this institution.  
We recognize that the University of Saskatchewan has one of the lowest graduate tuition  
rates amongst Canadian universities, but we  also recognize that the universities of many  
other wealthy nations require no tuition at all from their citizens. Not only do the citizens  
of  these  countries  benefit  from  this  opportunity  to  partake  in  higher  education,  but  the  
countries in which they live benefit from a “better quality of life” due in part to the effect  
of having a better-educated population. Given this, and given the disagreement that exists  
on campus regarding spending priorities, the GSA believes that there are alternatives to  
tuition increases for balancing our institution’s budget.  

Saskatoon  has  seen  a  dramatic  cost-of-living  increase  in  recent  years  that  negatively  
impacts  the  ability  of  graduate  students  to  afford  education.  Increasing  costs  for  food,  
transportation, and accommodation in the city of Saskatoon are leading to an increased  
financial burden for all students. An increase in tuition will only compound this burden  
and  push  students  away.  An  increased  financial  burden  does  not  just  mean  less  pocket  
money. It means many students who may otherwise be able to commit themselves fully to  
their studies will have to take additional employment. This is not just an inconvenience  
for students; this reduces the quality of scholarship coming out of the U of S.   

While one could argue that our lower tuition rates may not serve to bolster our prestige,  
the fact is that other universities can justify higher tuition only because they already have  
higher  scholarly  prestige.  Until  we  generate  the  prestige  to  put  us  on  par  with  more  
expensive universities, our lower costs will continue to be one of our key attractions.  

If the U of S wishes to become a competitor amongst Canada’s top schools, it needs to  
foster  an  environment  conducive  to  higher  quality  scholarship.  Scholars  are  most  
productive and progressive when they are free to focus all of their attention on their work.  
This demands both that they have access to the resources and facilities they require and  

                                 Graduate Students’ Association  

                               Position Statements Policy Manual  

                                                 9-3  

----------------------- Page 4-----------------------

that they be as free as possible of extraneous constraints. Tuition is exactly the sort of  
barrier this university should be working to remove from the path of talented scholars. It  
is certainly not something to be increased.  

The GSA strongly believes that the Provincial Government needs to take a stronger role  
in supporting the financial needs of the University and should increase its contribution to  
the budgets of the University. The GSA also very firmly believes that increased tuition  
would reduce the diversity of voices among the scholars of this institution by placing a  
further  impediment  in  the  way  of  disadvantaged  populations  and  is  contrary  to  best  
interests of the university and the broader community.  

  

The GSA believes that the University should view graduate students as investments in the  
both the social and the economic future of our community and work to make sure that  
tuition:  

         i)        Be reduced annually with an end-goal of zero tuition.                       

         ii)       Be considered a barrier to education and not necessary.  

         iii)      Should be equitable and continue to be assessed without differential fees  
                   for international students.  

         iv)       Approached with leadership in mind rather than comparison.  

         v)        Increases  should  be  brought  to  the  student  body  before  approval  and  
                   implementation in the interests of transparency and legitimacy.  

                                    Graduate Students’ Association  

                                  Position Statements Policy Manual  

                                                      9-4  
