\section{Interpretation}
\subsection{Definitions} 
\subsubsection {}The following definitions clarify terminology in the constitution, unless context suggests otherwise. 
\begin{enumerate}[i]
\item Academic Councils – ratified student groups representing academic units in accordance with 5.1. 
\item Annual Operating Budget – a budget detailing line by line the sums spent or received to a given account within the GSA. 
\item Association – the Graduate Students’ Association may also be referred to as the Association. 
\item Chair Electoral Officer – see policy 2.1.1 
\item Executive – the body which is comprised of the President, the Vice-Presidents and the Aboriginal Liaison 
\item GSA Council – the group of registered ratifies student representatives from all schools or departments. Academic Councils within the CGSR that comprise the authoritative decision-making entity of the GSA. 
\item  Representatives – ratified student representatives from each academic unit belonging to an Academic Council. 
\item  Social groups – ratified graduate student groups or clubs in accordance with policy 4.3.2.1. 
\end{enumerate}

\section{The Association and Executive of the Association }
\subsection{ The Association }
2.1.1. The name of the organization shall be the University of Saskatchewan Graduate Students’ Association, (the abbreviation of which is “GSA”, hereinafter also referred to as the Association). 

2.1.2. The purpose of the GSA shall be to: 
\begin{enumerate}[i]
\item Ensure its members have access to quality services that support their academic success, 
\item Advocate for the unique needs and concerns of its members, 
\item Build a cohesive community among its members. 
\end{enumerate}

2.1.3. The GSA is the representative of the graduate students of the University of Saskatchewan to the administration, faculty, and external Graduate Students’ Association community. It shall attempt to provide professional, academic, and social activities, promote awareness of issues relevant to graduate students, and provide services. 
\begin{enumerate}[i]
\item The GSA recognizes that every student has the right to equal treatment with respect to student activities and organizations, without discrimination because of race, ancestry, place of origin, colour, ethnic origin, citizenship, religion, creed, sex, sexual orientation, age, marital status, family status, disability or the receipt of public assistant. The association further recognizes that some students have been historically and systematically disadvantaged on the above grounds, with resultant under-representation in institutions of post-secondary 
education. The GSA shall strive to be free of all forms of discrimination in all endeavors. 
\item The GSA shall exert every reasonable effort to ensure the accessibility 
of its activities in accordance with the grounds outlined in subsection i). 
\item Pursuant to the approval of GSA Council, a right under subsection i) and/or subsection ii) is not infringed by the efforts of individuals or the formation and organization of groups designed to assist and support those students who have been the target of systematic discrimination pursuant to the grounds enumerated in subsection i) and shoes aim to achieve equal opportunity, or that is likely to contribute to the elimination of the infringement of rights under subsection i). 
\item The GSA shall strive to provide a stimulating and accessible educational experience at the University of Saskatchewan that promotes diversity of intellectual representation and perspective. 
\item Association policy shall be consistent and reflective of the items outlined in subsection i) to v) inclusive. 
vi) Section 2.1.3 i) shall be subject to evolve with the Canadian Charter of 
Rights and Freedoms. 
\end{enumerate}

2.1.4. The GSA shall have control over all legitimate student enterprises of a non-academic nature which fall within its own purview. 

2.1.5. The GSA shall be carried on without purpose of gain for its members 
and any profits or other accretions to the organization shall be used 
solely to promote the purpose of the organization as outlined in 2.1.2. 

2.1.6. This constitution shall take precedence over all other councils and 
student organizations to which GSA members belong, unless otherwise 
specified in this constitution. 
\subsection{The Executive of the Association }
2.2.1. The Executive of the GSA shall consist of a President, Vice-President (Student Affairs), Vice-President (Finance), Vice-President (External), 
Vice-President (Academic), Vice-President (Operations and Communications) and the Aboriginal Liaison. The executive shall be voting members of both the Executive Council and GSA Council. Executive terms shall run from May 1 to April 30. 
2.2.2. The Executive shall run individually and shall be elected by the student body at large. The campaign and election shall be held in accordance with the Policy 2. Elections and Referenda. Individuals running for Executive member positions must be members during their term in office. 
2.2.3. In the absence or unavailability of any one member of the Executive the remaining Executive members may appoint a replacement, who is an association member, subject to the approval of the two-thirds (2/3) of the members of the GSA Council present and voting at a meeting where notice of a motion of approval has been duly given. Should the nominee be rejected, the GSA Council may make an appointment, or require the remaining Executive members to propose alternative nominees. 
2.2.4. Should the GSA Council decide that the exercising of its authority to nominate candidates is undesirable, it shall call an election to be held in accordance with Policy 2. Elections and Referenda. 
2.2.5. In the absence or unavailability of more than one member of the 
Executive or in the event that all offices become vacant, the GSA 
Council shall choose replacements whoc shall assume the powers and 
duties of those Executive members. An election shall be held as soon 
as is feasible, in accordance with Policy 2. Elections and Referenda. 
2.2.6. Duties of the Executive are listed in Policy 1. Executive Duties. 
\subsection{Removal of the Executive members }
2.3.1. The President and Vice-Presidents may be removed from office 
individually, however more than one may be removed at a time 
2.3.2. Such removal may be enacted by: 
i) A non-confidence vote by GSA Council. Such a vote must be the 
result of a motion that has had at least two weeks written notice to all GSA Council members. To be resolved the non-confidence motion 
must be passed by a two-thirds (2/3) majority of the total membership 
of GSA Council; or 
ii) A referendum to impeach. Such a referendum shall be received at any 
time by GSA Council and must be supported by the signatures of two 
percent (2\%) of the members of the GSA. Such a referendum shall be 
conducted by the Chief Electoral Officer on a date selected by him/her, 
separate from any other election or referendum. At least a two week 
notice of the referendum must be given to GSA members via posters 
and a website update but in no instance shall more than one month 
pass between submission of the impeachment papers and the date of 
the balloting. 
2.3.3. If a non-confidence vote or an impeachment referendum is resolved in 
the affirmative, the GSA Council shall proceed under Policy 2. 
Elections and Referenda to elect a new Executive member(s) so that 
not more than one month passes before the new President and/or Vice- 
Presidents take office. Throughout the interim period the duties of the 
Executive shall be carried out by such person or persons as appointed 
by the GSA Council. 
2.3.4. In the event of a resignation, the resignation of a vice president of the 
Executive shall be considered tendered when given to the President. In 
the event the President is resigning, resignation shall be given to GSA 
Council. Resignations including written or email are valid. 
\section{ Aboriginal \& Indigenous Graduate Student Council }
\subsection{Aboriginal \& Indigenous Graduate Student Council }
3.1.1. The GSA within its organizational capacity will support the Aboriginal 
\& Indigenous Graduate Student Council (AIGSC) in representing the 
unique nature of issues relevant to its membership. 
3.1.2. Notwithstanding 3.1.1 in an event where each organization’s mandate 
is conflicting on an issue the GSA must take priority in representing 
the student body at large. 
\subsection{Aboriginal Student Liaison}
3.2.1. An Aboriginal Student Liaison will be appointed by the Aboriginal \& 
Indigenous Graduate Student Council which will follow the duties as outline 
in Policy 1. Executive Duties. 
3.2.2. The Aboriginal Student Liaison will be supervised by the AIGSC. 
Removal or changes to the position’s mandate will be at the AIGSA’s 
discretion. 
\section{Membership and Fees }
\subsection{Members }
4.1.1. Members of the association shall be regular members only. 
i) Regular members shall be all graduate students registered in the 
College of Graduate Studies and Research (CGSR). 
ii) Post-doctoral fellows and graduate student members of the Saskatoon 
Theological Union may become regular members if they register with 
the College of Graduate Studies and Research and pay the full GSA 
fees. 
4.1.2. Each member may belong to a member Academic Council as well as 
the GSA Council. He/she may enjoy the rights and privileges of both 
organizations. 
4.1.3. Students may be a member of both the Aboriginal \& Indigenous 
Graduate Student Council (AIGSC) and any Academic Council 
representing a school of the CGSR. 
 
\subsection{Rights, Privileges and Obligations }
4.2.1. The rights and privileges of regular members shall be: 
i) To vote on all GSA elections and referenda; 
ii) To hold offices or positions of employment within the GSA; 
iii) To attend meetings of the GSA subject to the rules and procedures of 
this constitution; 
iv) To move or second motions at such meetings; 
v) To speak for or against a motion; 
vi) To vote at GSA Annual General Meetings or Special General 
Meetings ; 
vii) To gain admission to and/or actively participate in any GSA sponsored 
event and/or program subject to the restrictions of that particular event 
and/or program. 
4.2.2. Except as may be directed by GSA Council with regards to the GSA 
Operations Budget, no members is empowered to make purchases in 
the name of the GSA or in any other way financially obligate the GSA 
until permission has been granted by the Board. 
4.2.3. Members may tender a resignation in writing, which shall be effective 
upon acceptance thereof by GSA Council. In the case of resignation, a member shall remain liable for payment of any assessment or other 
sum levied or which became payable by him/her to the GSA prior to 
acceptance of his/her resignation. 
\subsection{Fees }
4.3.1. GSA members shall be charged an annual fee to fund operations of the 
organization. The University of Saskatchewan shall be empowered to 
collect from all GSA members. The GSA Council shall be responsible 
for ensuring that said fees are expended in a manner consistent with 
the purpose of the organization. 
4.3.2. At a GSA Council meeting in December, GSA Council shall approve 
the GSA fee for the next fiscal year. A fee will be proposed by the 
GSA Executive and must pass a two-thirds (2/3) vote of GSA Council. 
4.3.3. The GSA fee may be increased by no more than 5\% plus the previous 
year’s Consumer Price Index (CPI) without a referendum of the 
student body as outlined in Section 13 of this Constitution. 
\section{GSA Council }
\subsection{Membership }
5.1.1. Voting members of GSA Council shall be the GSA Executive and 
ratified Representatives from the Academic Councils. The number of 
Representatives allocated to each Academic Council is established in 
section 5.1.6. 
5.1.2. Any school or department within the College of Graduate Studies and 
Research is entitled to have representation on GSA Council. 
5.1.3. Each school or department within the CGSR may have only one 
Academic Council. Representatives from the member council shall be 
chosen in a manner determined by the member council. No 
representative shall represent both a school of the CGSR and the 
Aboriginal Indigenous Graduate Student Council (AIGSC). 
5.1.4. The AIGSC will also be included as a member of GSA Council and 
will be granted representation as outlined by section 4.1.5. 
5.1.5. A college may have a coherent Academic Council under the conditions 
of 5.1.3, and where any department within that College may have a 
separate Academic Council. 
5.1.6. The number of Representatives for future Councils will be based on 
the enrolment numbers of the previous year provided by the Academic 
Councils at the earliest possible convenience. Representative allocation for each Academic Council will be: 
i) One representative from each Academic Council with up to 24 
graduate students, 
ii) Two representative from each Academic Council with up to 25 to 49 
graduate students, 
iii) Three representatives from each Academic Council with 50 to 99 
graduate students, 
iv) Four representatives from each Academic Council with 100 to 149 
graduate students, 
v) Five representatives from each Academic Council with 150 to 199 
graduate students, 
vi) Six representatives from each Academic Council with 200 to 249 
graduate students, 
vii) Seven representatives from each Academic Council with 250 or more 
graduate students. 
\subsection{Terms of Reference of the GSA Council }
5.2.1. The GSA Council is the ultimate decision-making body for the policy 
and political affairs of the GSA. GSACouncil has full power, within 
the restrictions of this Constitution, to create, alter and/or terminate 
any policy statements, which are considered to be GSA Policy, and to 
deal with any reports, recommendations and/or conclusions of any 
groups, committees and organizations which fall within the purview of 
the GSA. 
5.2.2. Without in any way restricting the generality of the foregoing, GSA 
Council shall aim to fulfil its mandate by debating and dealing with 
any reports, including their recommendations and conclusions; with 
motions, as submitted by the GSA Executive, GSA Council or the 
student body at large; and with policy decisions regarding the official 
stance of the GSA on any issue within the purview of GSA Council. 
GSA Council shall also be empowered to direct the Executive to 
represent the GSA where it is deemed necessary, and to carry out 
various duties in the interest of the student body. 
5.2.3. In all debate and decision-making the GSA Council shall be guided, as 
far as possible, by the objects contained in this Constitution. 
5.2.4. GSA Council shall have the authority, except as otherwise specified, to 
appoint representatives of the GSA to any committees, commissions, 
boards etc.
\subsection{Election and Removal of GSA Council Members }
5.3.1. With the exception of the GSA Executive, the members of the Council 
shall be elected by their respective organizations according to the rules 
and regulations for the election of Council members, as specified by 
the individual faculty Academic Councils. 
5.3.2. Each Academic Council member is expected to act in the best interest 
of their constituency. 
5.3.3. All Academic Council members are subject to removal under 
subsection 5.3.4 on the following grounds: 
i) Absence from four (4) or more duly called meetings; 
ii) Just cause; 
iii) Theft, fraud or embezzlement of funds; 
iv) Ineligibility to be a member. 
5.3.4. Members of the GSA Council can only be removed by the faculty 
association which they represent, according to the procedure for 
impeachment which governs that school or department’s student 
association. The Chairperson of GSA Council, however, is charged 
with formally notifying both GSA Council and the appropriate faculty 
association of a voting council member's breach of subsection 5.5.3. 
Furthermore, GSA Council may make recommendations to the 
respective faculty association so that appropriate action is taken . 
5.3.5. Notwithstanding that, by virtue of subsection 5.3.4, GSA Council 
members may only be removed from the GSA by the faculty 
association which they represent, upon notifying GSA Council of a 
voting member's breach of subsection 5.3.3 the Chairperson shall 
move a motion, which has had proper notice, that the offending 
Council member's voting rights be denied. If such a motion is 
approved by a majority of GSA Council members present and voting 
then the offending GSA Council member shall be denied his/her vote 
from there forward. A GSA Council member denied his/her vote in 
accordance with this subsection shall retain all other rights associated 
with GSA Council membership but shall not be counted in quorum. 
The GSA Council may reinstate at any time in the future a GSA 
Council member's vote which has been denied. 
5.3.6. Subsection 5.3.4 does not apply to the Executive of the Association, 
whose removal from office is governed by Section 2.3. 
5.4. GSA Council Meetings and Quorum 
5.4.1. The reference source for all points of order to produce shall be 
Robert’s Rules of Order, revised in its most recent edition. 
5.4.2. GSA Council will meet on a monthly basis. Meetings will be held in 
accordance with the Rules of Order as outlined in Policy 5. Meetings. 
5.4.3. GSA Council meetings will be chaired by a Chairperson, whose 
responsibilities will also include acting as the Chief Electoral Officer 
and Chief Returning Officer. 
5.4.4. The Vice President Operations and Communications shall be 
responsible for keeping minutes of all regular meetings of the GSA 
Council and for ensuring the duplication and distribution of all 
minutes, papers and reports or other documents to GSA Council 
members as outlined in Policy 3. Communications. 
5.4.5. The meetings of the GSA Council shall be open to the public; 
however, there shall be GSA to closed sessions if so decided by a 
majority of the members present. If a closed session is held, the reason 
therefore shall be announced immediately following the closed 
session. 
5.4.6. A fifty percent (50\%) majority plus one of voting GSA Council 
members, not including proxy members, shall form a quorum for the 
transaction of business. If quorum is not maintained, the meeting shall 
be adjourned and the time and names of members still present shall be 
recorded in the minutes. Alternate members are not permitted to vote 
in GSA Council as stated in reference source for all points of order 
declared in 5.4.1. 
5.4.7. All motions of the GSA Council shall be decided by a majority vote, 
with each Representative and Executive member entitled to one vote. 
In the case of an equality of votes, the Chairperson shall cast the 
deciding vote. All votes at such meetings shall be taken by ballot with 
the approval of the Chairperson, or the support of a majority of GSA 
Council members present. If no demand is made, the vote shall be 
taken in the usual way by a show of hands. 
5.4.8. Any GSA Council meeting shall adjourn at a point no later two (2) 
hours after the time when it was scheduled to begin, less a motion to 
extend by thirty (30) minutes is passed by a two/thirds (2/3) majority 
at each thirty (30) minute interval for a maximum of two (2) intervals. 
5.4.9. All GSA Council Meetings will be recorded and publicized in accordance with Policies 3. Communication and 5. Meetings. 
\subsection{Notice of GSA Council Meetings }
5.5.1. The President or any Vice-President of the Association shall have the 
power to call, at any time, a special meeting of GSA Council. Further, 
such meetings shall be called by a student at large upon receipt of a 
petition to do so signed by ten (10) GSA Council Members. Notice of 
a special meeting of GSA Council shall be forty-eight (48) hours. 
5.5.2. Notwithstanding subsection 5.4.5, the President of the GSA, in the 
case of an emergency, may call a special meeting of GSA Council at 
any time without being subject to the forty-eight (48) hour notice 
requirement. 
\section{Academic Councils }
\subsection{Funding }
6.1.1. In order to qualify for funding, Academic Council must: 
i) Have an updated constitution on file with the GSA, 
ii) Have an updated membership list, 
iii) Have a GSA council bank account where at least two GSA Council 
members must sign all transactions which debit the account, 
iv) Submit a written request for funding to the VP Finance, 
v) Have a ratified representative in GSA Council, 
vi) Have a list of their executive members and contact information, 
vii) Actively fulfill its constitutional duties to its respective members 
6.1.2. Academic Councils will be funded by GSA fees as outlined in Policy 5. Finances 
6.1.3. All ratified Academic Councils are eligible to request for additional 
funding by submitting a written request for additional funding to the 
Vice-President (VP Finance). 
\subsection{Alternates for Academic Council members are not eligible to vote 
 in GSA Council meetings in agreement with 5.4.1. }
\section{Financials }
\subsection{Budgeting }
7.1.1. The fiscal year of the organization will run from May 1 to April 30. At 
the end of the closing year an annual budget will be prepared to 
summarize the previous year’s financial activity. 
7.1.2. The annual operating budget, starting May 1, will be approved at the 
Annual General Meeting in April of the previous fiscal year. It will be 
created with recommendations from all GSA Executive that are in 
office during the April Annual General Meeting. The annual operating 
budget must include with it the breakdown of expenditures and 
revenues that will occur each month in the same line items appearing 
the annual operating budget. 
7.1.3. A monthly budget will be presented to GSA Council each month 
outlining the revenues and expenditures accrued during the previous 
month, this budget will be delivered at the GSA Council meeting. 
7.1.4. Monthly budgets should include the actual year-to-date, budgeted 
year-to-date and budgeted year total for each line item. 
7.2. Accounting practices 
7.2.1. Under no circumstances will the annual operating budget , approved 
by GSA Council, be adjusted by the Executive without a motion in a 
GSA Council meeting supported by a two-thirds (2/3) vote. 
7.2.2. Any auditor hired to review the GSA financials must be approved by a 
two-thirds (2/3) vote of GSA course Council. 
7.2.3. In all circumstances the use of a miscellaneousline item is 
discouraged. Only in circumstances where expenditures or revenues 
cannot be traced shall funds be allocated to a miscellaneous account. 
7.2.4. All revenues or expenditures must be allocated to line items within the 
budget that best represent their nature. 
\section{Committees }
8.1.1. Standing committees are established to consider continuing questions. 
Once established they shall serve continuously with progressive 
changes in membership. The committee shall continue to exist until 
otherwise decided by Course Council. 
8.1.2. Special committees are established for the purpose of examining 
questions when no appropriate standing committee exists. Their 
memberships and terms of reference shall be determined by a 
resolution of Course Council. A special committee shall be considered 
disbanded following the reception of its final report by Course 
Council. 
8.1.3. The terms of reference of any committee are set by Course Council 
and may only be extended or reduced by Course Council through a 
motion with proper notice. 
8.1.4. The opinions and expressed views and policies of GSA Committees 
are not necessarily those of Course Council. 
8.1.5. The Chairperson of each committee shall be elected by the 
membership of the Committee, usually from the membership of the 
committee unless otherwise directed. 
8.1.6. All committee appointments shall be made and/or ratified by Course 
Council. 
8.1.7. Committees are required to present progress reports and working 
papers, verbally or in a written statement, to Course Council, and 
should Course Council feel that the committee is neglecting its duties, 
it shall take whatever action is considered appropriate. 
8.1.8. A committee report, which shall be presented to Course Council by the 
Chairperson, shall reflect the majority opinion of the committee. 
8.1.9. Reports and their accompanying recommendations may be received by 
a motion of Course Council. Any report not received shall be 
considered not to exist. 
8.1.10. Reports may be approved in principle, separate from their 
accompanying recommendations, by a motion of Course Council. A 
report that is received according to subsection 8.1.9 does not 
necessarily have to be approved. Reports are approved in principle 
while their recommendations are approved separately as specific 
policy resolutions. Should there be more than one recommendation, 
they shall be considered for approval on an individual basis, and 
Course Council shall only be bound by those recommendations that 
are approved. A report without any recommendations requires no 
further proceedings with reference to it, subsequent to its reception and 
approval in principle, except on the direction of Course Council. 
8.1.11. Without in any way limiting the generality of the foregoing, seven 
(7) standing committees of the Association shall include: 
i) Budget Planning Committee 
a. GSA President 
b. VP Finance 
c. At least 2 Academic Councilors 
ii) Bursary Selection Committee 
a. GSA President 
b. VP Finance 
c. VP Academic 
d. At least 2 Academic Councilors 
iii) Elections and Referenda Committee 
a. GSA President 
b. VP Operations 
c. CEO (Chair Electoral Officer) 
iv) Constitution Review Committee 
a. GSA President 
b. VP External Affairs 
c. At least 2 Academic Councilors 
v) Code of Ethics and Discipline Committee 
a. CEO (Chair Electoral Officer) 
b. GSA President 
c. At least 1 Academic Councilor 
d. At least 1 GSA member who is not an Executive or Academic 
 Councilor 
vi) Travel Grant Committee 
a. VP Finance 
b. VP Academic 
c. At least 2 Academic Council members 
vii) Gala Committee 
a. 2 GSA Executives chosen by the GSA President 
b. At least 2 Academic Council members 
\section{ Association Annual General Meetings and Association Special  Meetings }
\subsection{General} 
9.1.1. There shall be two (2) types of meetings of the GSA members: Annual 
General Meetings and Special General Meetings. 
9.1.2. Annual General Meetings and Special General Meetings shall be held 
on the campus of the University in a location determined by the GSA 
Council. Such meetings shall be chaired by the Chairperson of the GSA Council. 
9.1.3. Annual General Meetings and Special General Meetings will be held 
in accordance with Policy 5. Meetings. 
9.1.4. Annual General Meetings and Special General Meetings may, from 
time to time, be adjourned to any future time or to a different place. 
Such business may be transacted at such future meeting as might have 
been transacted at the original meeting from which such adjournment 
took place. No notice shall be required for the motion for adjournment. 
The motion for adjournment may be made notwithstanding that no 
quorum is present. 
9.1.5. All members of the GSA: 
i) may be present at any Annual General Meetings and Special General 
Meetings; 
ii) may speak to any motion under consideration; 
iii) may move or second motions; 
iv) may exercise their voting privileges. 
9.1.6. Each member of the GSA shall be entitled to one vote at Annual 
General Meetings and Special General Meetings. 
9.1.7. Motions at all Annual General Meetings and Special General Meetings 
shall be decided by a majority of votes present in person unless 
otherwise required by this Constitution. All votes at such meetings 
shall be taken by ballot if so demanded by any member present, but if 
no such demand be made, the vote shall be taken by hands. A 
declaration by the Chair that a resolution has been carried or not 
carried, and an entry to that effect in the minutes of the meeting shall 
be admissible in evidence as prima facie proof of the fact without 
proof of the number or proportion of the votes accorded in favour of or 
against such resolution. Should a ballot be demanded, it shall be taken 
in such a manner as the Chair shall direct. In the case of an equality of 
votes, the Chair shall be entitled to a second or deciding vote. In such 
cases, the Chair shall vote to maintain the status quo where possible. 
9.1.8. Notice of the time and place of Annual General Meetings and Special 
General Meetings shall be given by posting the location and time on 
the GSA website and posting flyers throughout campus. 
9.1.9. Quorum at Annual General Meetings and Special General Meetings 
shall be fifty (50) members of the GSA. Should there be no quorum at 
such a meeting, business may proceed as usual; all decisions made shall be binding, except as follows: 
i) Should any members of the GSA disagree with any decision made at 
the meeting they may present a petition containing the signatures of 
one hundred (100) members of the GSA asking for a replacement 
Special General Meeting; 
ii) The petition shall only be received within two (2) weeks after the 
adjournment of the impugned meeting; 
iii) The replacement Special General Meeting shall be held within one (1) 
week of the receipt of the petition; 
iv) The quorum at such a replacement Special General Meeting shall be 
fifty (50) members of the GSA, and if present the replacement Special 
General Meeting may review any decision of the impugned meeting 
and by a majority vote confirm or reject it; 
v) If no quorum is present the replacement Special General Meeting 
cannot convene and the decisions of the impugned meeting shall 
become binding. 
9.1.10. Any GSA member may place a motion on the agenda for Annual 
General Meetings and Special General Meetings provided that: 
i) there is a mover and a seconder who are both GSA members; and 
ii) the motion with mover and seconder is submitted in writing to the 
President on or before the seventh (7th) day before the day of the 
meeting. 
9.1.11. The agenda for all Annual General Meetings and Special General 
Meetings shall be available to all GSA members at least one week 
before the day of the meeting. 
9.1.12. Motions may be added to the agenda by presenting the motion to 
the Chair at the beginning of the Annual General Meeting and Special 
General Meeting. The motion will be accepted if: 
i) it is the Chair's opinion that there were reasonable circumstances 
which prevented the motion from being submitted before the agenda 
deadline; or 
ii) a two-thirds (2/3) majority of the members present at the meeting 
agree to consider the motion. 
9.1.13. Unless otherwise specified, Annual General Meetings and Special 
General Meetings may deal with any matters normally dealt with by 
GSA Council. The decisions of Annual General Meetings and Special 
General Meetings shall be binding in GSA Council Policy. 
\subsection{Annual General Meetings }
9.2.1. The Annual General Meeting shall be held in April every year. The 
date of such meeting must be after the Executive elections. 
\subsection{Special General Meetings }
9.3.1. The President or Vice-President of the Association shall have the 
power to call, at any time, an Special General Meeting. Such meetings 
may also be called at the discretion of GSA Council or shall be called 
upon receipt by the President of a petition to do so signed by one- 
hundred (100) members of the GSA. 
\section{Rights, Privileges and Obligations of Member Association }
10.1.1. The member associations shall recognize the obligations, powers 
and jurisdiction of the GSA as granted by this Constitution. 
10.1.2. The GSA shall exercise its jurisdiction under subsection 2.1.6 over 
the member associations only in extreme circumstances. If an action 
by the GSA in this regard is opposed by a member association, it shall 
only be achieved and implemented by a two-thirds (2/3) vote of the 
total membership of GSA Council. 
10.1.3. While member associations are primarily responsible to their 
respective faculties, they also recognize their responsibility to all 
students at the University and to the GSA as the student government at 
the University. 
10.1.4. The GSA recognizes the specified rights, privileges and obligations 
which are beyond the jurisdiction of the GSA. These rights, privileges 
and obligations shall include, but shall not be limited to, the following: 
i) Every member association has jurisdiction over its own governmental 
structure, and its aims and purposes. As a consequence, member 
associations shall have authority to amend their constitution, to 
administer and regulate their own elections, and shall control the 
selection and tenure of their representatives on GSA Council; 
ii) Every member association has jurisdiction over its own policies; 
iii) Every member association has jurisdiction over its own finances and 
their administration. The member association shall have full control 
over their budget and any respective fees. 
iv) Every member association has the authority: 
a. To send representatives to GSA Council meeting 
b. To ensure the GSA Executive is held accountable to the 
 Constitution. 
c. To run social events subject to the guidelines in this Constitution; 
d. To publish any publication it wishes; 
e. To administer, regulate and control its own physical space in 
 accordance with the regulations of the University and, where 
 applicable, the GSA; 
v) Every member association shall have authority over and responsibility 
for its own orientation program as regards policies, programs, 
regulations and specific events. 
vi) Every member association has the right to prior consultation regarding 
any GSA Policies or constitutional amendments which might affect the member association, before such policies or constitutional 
amendments are presented to GSA Council. 
\section{Transition }
11.1.1. The Executive shall be retired at the close of their one year term in 
office. At that time the Executive-Elect shall assume the powers vested 
in the offices of the Executive. 
11.1.2. In accordance with Policy 3. Communication the Executive, prior 
to the election of their successors, shall ensure that the Transition 
Manual is up to date. Further, during the Transition period, the 
Executive-Elect shall refer to said Transition Manual. 
\section{Amendments }
\subsection{Constitutional Amendments }
12.1.1. Unless otherwise stated in this Constitution, any part, section, 
subsection or paragraph of this Constitution may only be amended at 
an Annual General Meeting or Special General Meeting, or by a 
referendum of the membership as outlined in section 13 of this 
Constitution. 
12.1.2. Amendments required because an organization referred to in this 
Constitution has undergone a name change, become defunct, or have 
otherwise left the GSA, shall be considered housekeeping and may be 
entered as a matter of course by the Vice President External. The Vice 
President External shall notify GSA Council of any such amendments. 
12.1.3. All amendments or changes to this Constitution shall be published 
in an update version of the constitution on the GSA website in 
accordance with Policy 3. Communication two weeks after been ratified. 
12.1.4. Until such amendment is given effect, this Constitution shall 
remain in force and be binding upon the GSA as regards any party 
acting on the faith thereof. 
12.2. Policy Manual Amendments 
12.2.1. Policy manuals may be amended at any GSA Council meeting were 
due notice has been given. Amendments to policy manuals must pass a 
two-thirds (2/3) vote by GSA Council. 
\section{ Canadian Federation of Students} 
13.1.1. The GSA shall budget for and send appropriately sized delegations 
to all CFS national meetings, including but not limited to the May 
Semi-Annual meeting, the November Annual meeting, the National 
Graduate Caucus Stand-Alone and the National Aboriginal Caucus 
Stand-Alone meeting. This shall happen through a discussion leading 
to a consensus at the GSA executive level or if needed, by an 
executive vote in the regular executive meetings. The Council 
approval is required if more than four (4) delegates are to be sent to 
any of these meetings. 
13.1.2. The GSA shall budget for and send appropriately sized delegations 
to all CFS Saskatchewan provincial meetings. 
\section{Elections and Referenda }
14.1.1. The GSA Chief Returning Officer/Chief Electoral Officer, in the 
final instance, shall be responsible for all GSA elections and referenda. 
The Chairperson of the GSA Council shall be the Chief Returning 
Officer and Chief Electoral Officer. 
14.1.2. The Chief Returning Officer/Chief Electoral Officer, who shall be 
appointed by the Vice President Operations and Communications, 
subject to ratification by GSA Council, shall be generally responsible 
for the administration of all GSA elections and referenda. Without 
limiting the generality of the foregoing, the duties of the Chief 
Returning Officer/Chief Electoral Officer shall be: 
i) To print posters; 
ii) To ensure that there is notification of an election or referendum in on 
the GSA website one week in advance. 
14.1.3. The Chief Returning Officer/Chief Electoral Officer shall announce 
the results of an election or referendum to the candidates involved 
immediately after they become known. The results may be made public only after notification has been given to the candidates. Should 
the candidates not be immediately available, the results would be made 
public no less than two (2) hours after the results have been confirmed 
by the Chief Returning Officer or the Chief Electoral Officer. 
14.1.4. The Chief Returning Officer/Chief Electoral Officer shall vote 
twenty-four (24) hours in advance and place their ballot in a sealed 
envelope to be deposited with the Vice President Operations and 
Communications. This envelope will be opened only in the case of a 
tie vote. Should there be more than two candidates, or teams of 
candidates, the Chief Returning Officer/Chief Electoral Officer shall 
indicate their order of preference on the ballot form. 
14.1.5. All campaigns for elections and for referenda shall be run in 
conjunction with Policy 2. Elections and Referenda. Complaints 
regarding the violation of these regulations shall be brought to the 
attention of the Chief Returning Officer/Chief Electoral Officer, and, if 
they feels it is necessary, GSA Council. Complaints must be in writing 
and must be brought forward no later than seventy-two (72) hours after 
the last poll closes. 
14.1.6. A referendum on any issue within the purview of the GSA or the 
member association may be called at any time by the GSA Council or 
by any member of the GSA. Questions may be placed on the 
referendum directly by GSA Council, or by a written request from any 
member of the GSA to the Chief Returning Officer/Chief Electoral 
Officer that is supported by signatures of at least two percent (2%) of 
current GSA members. 
14.1.7. The placement of all questions in the referendum shall be subject to 
GSA Council approval. Normally GSA Council shall approve any 
question that has garnered sufficient signatures in support; however, 
GSA Council shall retain the authority to reject any question where it 
finds compelling reason to believe that the passage of the question 
would constitute a violation of the mission or operating statement of 
the GSA; a violation of law; a contravention of University policy; a 
violation of contractual, financial or other obligations undertaken by 
the GSA; or would otherwise pose a significant threat to the best 
interests of the GSA or be injurious to the welfare of the graduate 
students at the University of Saskatchewan. Any such rejection shall 
require a two-thirds (2/3) vote in support from all voting members of 
GSA Council. 
14.1.8. The wording of all questions to be placed on any GSA referendum 
shall be subject to the approval of the GSA Council. GSA Council 
 shall have the authority to remove or amend misleading statements or 
 extraneous promotional content; correct errors of fact; and edit 
 technical errors of spelling and grammar. GSA Council shall not have 
 the authority to fundamentally change the substance of a question. 
14.1.9.Referenda decisions shall bind GSA policy, but shall not bind the 
 policy of member associations unless so provided in the individual 
 constitutions of the member councils. 